---
title: "Subtitle Frequency Counts"
author: "Erin M. Buchanan"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(readr)
library(stringi)
library(data.table)
library(dplyr)
library(rio)
```

First, this document pulls the **OpenSubtitles2024** monolingual dump directly from OPUS and builds unigram frequency counts from scratch. Two things come out of it, both consumed downstream:

- The raw decompressed subtitle text, saved to `open_subs/{lang_code}/{lang_code}.txt` -- this is what `03_diversity.rmd` reads.
- A unigram frequency count table, saved to `{lang_code}/{lang_code}_unigram_frequency.csv` -- this is what `02_phonemizer.rmd` reads.

## Language

Set this, then run the rest of the document for that language.

```{r language-params}
lang_code <- "uk"

subs_dir <- paste0("open_subs/", lang_code, "/")
lang_dir <- paste0(lang_code, "/")
dir.create(subs_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(lang_dir, recursive = TRUE, showWarnings = FALSE)

gz_path <- paste0(subs_dir, lang_code, ".txt.gz")
txt_path <- paste0(subs_dir, lang_code, ".txt")
count_path <- paste0(lang_dir, lang_code, "_unigram_frequency.csv")
```

## Download

OPUS hosts OpenSubtitles2024 as one monolingual file per language (one subtitle line per row, already deduplicated at the subtitle-file level upstream). If the language you're after 404s at this URL, check the language code against <https://opus.nlpl.eu/OpenSubtitles/corpus/version/OpenSubtitles> -- most use the two-letter code, but a few (e.g. Chinese, Portuguese) are split by variant.

```{r download}
subs_url <- paste0("https://object.pouta.csc.fi/OPUS-OpenSubtitles/v2024/mono/", lang_code, ".txt.gz")

if (!file.exists(gz_path)) {
  message("Downloading ", subs_url)
  download.file(subs_url, destfile = gz_path, mode = "wb")
}

file.info(gz_path)$size / 1e6  # size in MB, sanity check it's not an error page
```

## Decompress

Streamed through in chunks rather than reading the whole thing into memory at once -- these dumps can be a few hundred MB compressed, well over 1GB decompressed.

```{r decompress}
if (!file.exists(txt_path)) {
  con_in <- gzfile(gz_path, "rt", encoding = "UTF-8")
  con_out <- file(txt_path, "wt", encoding = "UTF-8")

  repeat {
    chunk <- readLines(con_in, n = 200000)
    if (length(chunk) == 0) break
    writeLines(chunk, con_out, useBytes = TRUE)
  }

  close(con_in)
  close(con_out)
}

file.info(txt_path)$size / 1e6  # size in MB
```

## Tokenizer

Default path is Unicode-aware word extraction (`stringi::stri_extract_all_words`), which works fine for space-delimited languages and, via ICU's dictionary-based break iterator, for Thai too (checked against a sample -- it segments real Thai words correctly out of the box).

Chinese and Japanese don't get spaces *or* a working ICU dictionary segmenter: ICU splits Chinese into character-ish fragments (e.g. it cuts `图书馆` "library" into `图书` + `馆`) and mangles Japanese verb conjugations. Those two get a real segmenter instead, via reticulate: `jieba` for Chinese, `fugashi` (MeCab) for Japanese. `fugashi` segments at the morpheme level (standard practice for Japanese frequency lists -- e.g. it'll split a conjugated verb into stem + inflection), which is expected, not a bug.

```{r python-tokenizers}
library(reticulate)
py_require(c("jieba", "fugashi", "unidic-lite"))

jieba <- NULL
ja_tagger <- NULL

if (lang_code %in% c("zh", "zh_cn", "zh_tw", "zh_hk")) {
  jieba <- import("jieba")
} else if (lang_code == "ja") {
  fugashi <- import("fugashi")
  ja_tagger <- fugashi$Tagger()
}

tokenize_lines <- function(lines) {
  if (!is.null(jieba)) {
    words <- unlist(jieba$lcut(paste(lines, collapse = " ")))
  } else if (!is.null(ja_tagger)) {
    words <- vapply(ja_tagger$`__call__`(paste(lines, collapse = " ")),
                    function(w) w$surface, character(1))
  } else {
    words <- unlist(stringi::stri_extract_all_words(lines))
  }
  words <- stringi::stri_trans_tolower(words)
  words <- words[!is.na(words)]
  words[stringi::stri_detect_regex(words, "\\p{L}")]
}
```

## Tokenize and count

Processed in chunks and tabulated with `data.table` for speed on a multi-million-line file; drops tokens with no letters (pure numbers/punctuation survivors). For `zh`/`ja`, `chunk_size` may need to come down from the default if a single joined chunk gets too large for `jieba`/`fugashi` to process comfortably.

```{r tokenize-count}
con <- file(txt_path, "rt", encoding = "UTF-8")
chunk_size <- 200000
freq_chunks <- list()
lines_seen <- 0

repeat {
  lines <- readLines(con, n = chunk_size, encoding = "UTF-8")
  if (length(lines) == 0) break
  lines_seen <- lines_seen + length(lines)

  words <- tokenize_lines(lines)

  if (length(words)) {
    dt <- data.table(unigram = words)[, .N, by = unigram]
    freq_chunks[[length(freq_chunks) + 1]] <- dt
  }

  message("processed ", lines_seen, " lines")
}
close(con)

freq_all <- rbindlist(freq_chunks)[, .(unigram_freq = sum(N)), by = unigram]
setorder(freq_all, -unigram_freq)

nrow(freq_all)
head(freq_all, 20)
```

## Export

Written as CSV with a header (`unigram`, `unigram_freq`) -- tokens are word-boundary extracted so they'll never contain a comma, and CSV round-trips cleanly with `rio::import()`.

```{r export}
rio::export(freq_all, count_path)
count_path
```
