---
title: "Phonemizer"
author: "Erin M. Buchanan"
date: "`r Sys.Date()`"
output: html_document
---

## Libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
py_require(c("phonemizer", "python-dotenv", "pandas"))
# brew install espeak-ng

library(rio)
library(dplyr)
```

Espeak-ng's install paths differ per machine, so they're kept out of this
file. Copy `.env.example` to `.env` in this folder and fill in your own
paths (see the comments in that file) before running the chunk below.

```{python}
import os, math
import pandas as pd
from dotenv import load_dotenv
from phonemizer import phonemize
from phonemizer.separator import Separator

# loads PHONEMIZER_ESPEAK_LIBRARY / PHONEMIZER_ESPEAK_PATH / ESPEAK_PATH from .env
load_dotenv()
```

## Language

Set these two, then run the rest of the document for that language. `lang_code` is the project's two-letter code (matches the folder names used elsewhere in the repo, e.g. `01-Translation/05_final_languages/{lang_code}`). `lang_espeak` is the espeak-ng voice code, which doesn't always match `lang_code` (e.g. English is `en-us`, not `en` -- run `espeak-ng --voices` to look one up).

```{r language-params}
lang_code <- "uk"
lang_espeak <- "uk"

lang_dir <- paste0(lang_code, "/")
dir.create(lang_dir, recursive = TRUE, showWarnings = FALSE)
```

## Data Work

```{r data-work}
# import_subs(lang_code, "subs_count")
subs_DF <- rio::import(paste0(lang_dir, lang_code, "_unigram_frequency.csv"))
subs_DF <- subs_DF %>%
  # lower case
  # trim white space
  mutate(unigram = trimws(tolower(unigram))) %>%
  # get rid of empty cells
  filter(nchar(unigram) > 0) %>%
  group_by(unigram) %>%
  # sum duplicates
  mutate(unigram_freq = sum(unigram_freq)) %>%
  ungroup()

# find cutoff frequency at position 100,000
cutoff <- subs_DF %>%
  arrange(desc(unigram_freq)) %>%
  slice_head(n = 100000) %>%
  pull(unigram_freq) %>%
  min()

# filter all words at or above that cutoff
subs_DF_final <- subs_DF %>%
  filter(unigram_freq >= cutoff)
```

```{python phonemes}
# --------- settings ---------
OUT_CSV     = f"{r.lang_dir}{r.lang_code}_subs_phono.csv"
LANG        = r.lang_espeak
KEEP_STRESS = False         # usually False for distance metrics
CHUNK_SIZE  = 20000         # tweak for very large lexicons
# ----------------------------

# 1) Load (space/tab delimited, no header)
subs = r.subs_DF_final

# 2) Phonemize (space-separated phones for token-level edit distance)
sep = Separator(phone=" ", syllable="", word="")  # ← phone tokens separated by spaces

phon_all = []
for i in range(0, len(subs), CHUNK_SIZE):
    chunk = subs.iloc[i : i + CHUNK_SIZE]
    ph = phonemize(
        chunk["unigram"].tolist(),
        language=LANG,
        backend="espeak",
        strip=True,
        with_stress=KEEP_STRESS,
        separator=sep,
    )
    phon_all.extend(ph)

subs["phon"] = phon_all

# 3) Save
subs.to_csv(OUT_CSV, index=False)
print(f"Wrote {len(subs)} rows to {OUT_CSV}")
subs.head()
```

