---
title: "Russian Data Combination"
author: "Erin M. Buchanan - Addie Clark"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goals

First, the lexical level variables for each item pair (prime and target frequency, etc.) will be included in the regression equation (see Goal 1 description). Next, the subjective level variables for each item pair will be added to the equation, followed by the similarity statistics. Last, the LLM embeddings for each target will be included in the regression equation.

## Libraries

```{r}
library(dplyr)
library(semanticprimeR)
library(rio)
```

## Item Data

```{r}
data("primeData")
# filter to just russian
primeData <- primeData %>% 
  filter(language == "ru") %>% 
  filter(type == "item_data")

# only need this line if you don't have the dataset yet 
DF <- import_prime("ru_item_data.csv")
DF <- import("item_data/ru/ru_item_data.csv") %>% 
  filter(class == "word") %>% 
  select(word)
```


## Lexical Data

frequency open sub
word length

1) linguistic information including length, frequency, orthographic neighborhood, bigram frequency, orthographic and phonographic Levenshtein distance, and semantic diversity 

## Subjective Data

```{r}
data("labData")
labData <- labData %>% 
  filter(language == "Russian" | language == "Multiple") %>% 
  filter(type1 == "Words" | type1 == "Word Pairs")
```

### AOA 

- here take a note if they say which version 
- mostly want the subjective ones

- @Grigoriev2013
  - Range = ... 
  - Coverage =  114


```{r}
aoaData <- labData %>% 
  filter(aoa == 1)

#Grigoriev2013$word_russian <- tolower(Grigoriev2013$word_russian)
#Grigoriev2013 <- import_lab("Grigoriev2013")
Grigoriev2013 <- import("lab_data/Grigoriev2013.csv")


# join together 
aoaDF <- DF %>% 
  left_join(Grigoriev2013 %>% 
              select(word_russian, aoa_o_M_months),
            by = c("word" = "word_russian")) %>% 
  dplyr::rename(Grigoriev2013_M = aoa_o_M_months) 


# coverage
nrow(aoaDF) - sum(is.na(aoaDF$Grigoriev2013_M))   
```

### Imagine

- @Grigoriev2013
  - Range = ... 
  - Coverage = 113

```{r}
imageData <- labData %>% 
  filter(imagine == 1) 

#Grigoriev2013 <- import_lab("Grigoriev2013")
Grigoriev2013 <- import("lab_data/Grigoriev2013.csv")

# join together
imageDF <- DF %>%
   left_join(Grigoriev2013 %>%
               select(word_russian, imagine_M),
             by = c("word" = "word_russian")) %>%
   dplyr::rename(Grigoriev2013_M = imagine_M)

# coverage
nrow(imageDF) - sum(is.na(imageDF$Grigoriev2013_M))
```

### Concrete

- @  
  - Range = ... 
  - Coverage =  

```{r}
concreteData <- labData %>% 
  filter(concrete == 1)

#no russian concrete data 

#Kanske2010 <- import_lab("Kanske2010")
#Kanske2010 <- import("lab_data/Kanske2010.csv")
#Kanske2010$word_german <- tolower(Kanske2010$word_german)

# join together 
#concreteDF <- DF %>% 
#  left_join(Kanske2010 %>% 
#              select(word_german, concrete_M),
#            by = c("word" = "word_german")) %>% 
#  dplyr::rename(Kanske2010_M = concrete_M) 

# coverage
#nrow(concreteData) - sum(is.na(concreteDF$Kanske2010_M))

```



### Valence

- @: 
  - Range = 
  - Coverage = 

```{r}
valData <- labData %>% 
  filter(valence == 1)

#no russian valance data 

# #Moors2013 <- import_lab("Moors2013")
# Moors2013 <- import("lab_data/Moors2013.csv")

# # join together
# valDF <- DF %>%
#   left_join(Moors2013 %>%
#               select(word_dutch, valence_M),
#             by = c("word" = "word_dutch")) %>%
#   dplyr::rename(Moors2013_M = valence_M)

# # coverage
# nrow(valDF) - sum(is.na(valDF$Moors2013_M))
# nrow(valDF) - sum(is.na(valDF$Speed2017_M))
```

### Arousal

- @: 
  - Range = 
  - Coverage = 

```{r}
arouData <- labData %>% 
  filter(arousal == 1)

# no russian arousal data 

# #Moors2013 <- import_lab("Moors2013")
# Moors2013 <- import("lab_data/Moors2013.csv")
# 
# 
# # join together 
# arouDF <- DF %>% 
#   left_join(Moors2013 %>% 
#               select(word_dutch, arousal_M),
#             by = c("word" = "word_dutch")) %>% 
#   dplyr::rename(Moors2013_M = arousal_M) 
# 
# # coverage
# nrow(arouDF) - sum(is.na(arouDF$Moors2013_M))
```



  
### Familiar

- @Grigoriev2013  
  - Range = ... 
  - Coverage =  115

```{r}
familiarData <- labData %>% 
  filter(familiar == 1)

#Grigoriev2013 <- import_lab("Grigoriev2013")
Grigoriev2013 <- import("lab_data/Grigoriev2013.csv")

# join together
familiarDF <- DF %>%
  left_join(Grigoriev2013 %>%
              select(word_russian, familiar_M),
            by = c("word" = "word_russian")) %>%
  dplyr::rename(Grigoriev2013_M = familiar_M)


# coverage
nrow(familiarDF) - sum(is.na(familiarDF$Grigoriev2013_M))
```


## Similarity Statistics

## Priming

### Human Prime

```{r}
data("primeData")
# filter to just russian
primeData <- primeData %>% 
  filter(language == "ru") 

nl_prime <- import_prime("ru_prime_summary.csv")
nl_prime <- import("priming_data/ru/ru_prime_summary.csv")

nl_matched <- import_prime("ru_trial_unique.csv")
```

### BERT Priming

## Embeddings

## Combine

```{r}

```