---
title: "Ukrainian Data Combination"
author: "Erin M. Buchanan - Addie Clark"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(dplyr)
library(semanticprimeR)
library(reticulate)
library(rio)
source("../functions.R")
```

# Stimuli Requirements

First, the lexical level variables for each item pair (prime and target frequency, etc.) will be included in the regression equation (see Goal 1 description). Next, the subjective level variables for each item pair will be added to the equation, followed by the similarity statistics. Last, the LLM embeddings for each target will be included in the regression equation.

## Item Data

```{r}
# load translation
# convert to item data format
DF <- rio::import("../../01-Translation/05_final_languages/uk/uk_trials_final.csv") %>%
  filter(type == "related") %>%
  select(uk_cue, uk_target) %>%
  pivot_longer(cols = everything(),
               names_to = "type",
               values_to = "word") %>%
  select(word)
```

## Lexical Data

```{r}
# length
DF$length <- nchar(DF$word)

# frequency processed with phonemes
subs_DF <- rio::import("uk_subs_phono.csv") %>%
  unique()

DF <- DF %>% 
  left_join(subs_DF, by = c("word" = "unigram"))

# orthographic neighborhood
DF <- calc_neighbors(DF, subs_DF)

# bigram frequency
DF <- add_bigram_frequency(DF, subs_DF, weight = "unigram_freq")

# orthographic Levenshtein
DF <- add_orthographic_levenshtein(DF, subs_DF, k = 20, max_len_diff = 3)

# phonographic Levenshtein
DF <- add_phonographic_levenshtein(DF, k = 20, max_len_diff = 3)

# semantic diversity
DF <- DF %>% 
  left_join(
    rio::import("uk_semantic_diversity.csv") %>%
      select(-V1),
    by = c("word" = "term")
  )

# check out the NAs
```

## Subjective Data

Candidate sources are found automatically from `lab_variables_target_means.csv`: any row whose `word_column` is `word_ukrainian` names a norming dataset that includes Ukrainian words. Each row is then matched to one of the six subjective categories below by keyword in its `variable` name, the matching file is loaded and averaged by word, and when more than one source lands in the same category their values are averaged together. As of now no rows match Ukrainian, so every category below comes back empty (all `NA`) until we add our own collected norms.

```{r}
labData <- rio::import("../lab_variables_target_means.csv") %>%
  filter(word_column == "word_ukrainian")

# where the underlying norming datasets live
datasets_path <- "/Users/erinbuchanan/GitHub/Research/2_projects/SPAML/semanticprimeR/datasets/completed/"

# pull one variable column from one source file, averaged by word
get_subjective_source <- function(file, word_column, variable) {
  path <- paste0(datasets_path, file)
  if (!file.exists(path)) return(NULL)

  rio::import(path) %>%
    select(word = all_of(word_column), value = all_of(variable)) %>%
    filter(!is.na(word)) %>%
    mutate(value = as.numeric(value)) %>%
    group_by(word) %>%
    summarize(value = mean(value, na.rm = TRUE), .groups = "drop")
}

# combine every labData row whose `variable` matches `pattern` into one column
combine_subjective <- function(labData, pattern) {
  matches <- labData %>%
    filter(grepl(pattern, variable, ignore.case = TRUE))

  if (nrow(matches) == 0) {
    return(tibble(word = character(), value = numeric()))
  }

  purrr::pmap(matches, function(file, word_column, variable) {
    get_subjective_source(file, word_column, variable)
  }) %>%
    bind_rows() %>%
    group_by(word) %>%
    summarize(value = mean(value, na.rm = TRUE), .groups = "drop")
}
```

### AOA

```{r}
DF <- DF %>%
  left_join(combine_subjective(labData, "aoa") %>% rename(aoa = value), by = "word")
```

### Imageability

```{r}
DF <- DF %>%
  left_join(combine_subjective(labData, "image") %>% rename(image = value), by = "word")
```

### Concrete

```{r}
DF <- DF %>%
  left_join(combine_subjective(labData, "concrete") %>% rename(concrete = value), by = "word")
```

### Valence

```{r}
DF <- DF %>%
  left_join(combine_subjective(labData, "valence") %>% rename(valence = value), by = "word")
```

### Arousal

```{r}
DF <- DF %>%
  left_join(combine_subjective(labData, "arousal") %>% rename(arousal = value), by = "word")
```

### Familiar

```{r}
DF <- DF %>%
  left_join(combine_subjective(labData, "familiar") %>% rename(familiar = value), by = "word")
```

## Similarity Statistics

## Priming

### Human Prime

```{r}
# not ready yet 
```

### BERT Priming

## Embeddings

## Combine

```{r}

```

## Output Variable Match

```{r}
DF_var_match <- DF %>% 
  select(word, aoa, image, concrete, valence, arousal, familiar) %>% 
  mutate(across(-word, ~replace_na(.x, FALSE)))

rio::export(DF_var_match, "ukr_variables_normed.csv", row.names = F)
```