---
title: "Ukrainian Data Combination"
author: "Erin M. Buchanan - Addie Clark"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(dplyr)
library(semanticprimeR)
library(reticulate)
library(rio)
source("../functions.R")
```

# Stimuli Requirements

First, the lexical level variables for each item pair (prime and target frequency, etc.) will be included in the regression equation (see Goal 1 description). Next, the subjective level variables for each item pair will be added to the equation, followed by the similarity statistics. Last, the LLM embeddings for each target will be included in the regression equation.

## Item Data

```{r}
# load translation
# convert to item data format
DF <- rio::import("../../01-Translation/05_final_languages/uk/uk_trials_final.csv") %>%
  filter(type == "related") %>%
  select(uk_cue, uk_target) %>%
  pivot_longer(cols = everything(),
               names_to = "type",
               values_to = "word") %>%
  select(word)
```

## Lexical Data

```{r}
# length
DF$length <- nchar(DF$word)

# frequency processed with phonemes
subs_DF <- rio::import("uk_subs_phono.csv") %>%
  unique()

DF <- DF %>% 
  left_join(subs_DF, by = c("word" = "unigram"))

# orthographic neighborhood
DF <- calc_neighbors(DF, subs_DF)

# bigram frequency
DF <- add_bigram_frequency(DF, subs_DF, weight = "unigram_freq")

# orthographic Levenshtein
DF <- add_orthographic_levenshtein(DF, subs_DF, k = 20, max_len_diff = 3)

# phonographic Levenshtein
DF <- add_phonographic_levenshtein(DF, k = 20, max_len_diff = 3)

# semantic diversity -- 03_diversity.rmd can take a long time to run over the
# full subtitle corpus, so this join is skipped (leaving no semdiv columns,
# rather than erroring) if that file isn't ready yet; rerun this chunk once
# uk_semantic_diversity.csv exists to backfill the real values
if (file.exists("uk_semantic_diversity.csv")) {
  DF <- DF %>%
    left_join(
      rio::import("uk_semantic_diversity.csv") %>%
        select(-V1),
      by = c("word" = "term")
    )
} else {
  message("uk_semantic_diversity.csv not found yet (03_diversity.rmd still running) -- skipping for now")
}

# check out the NAs
```

## Subjective Data

Candidate sources are found automatically from `lab_variables_target_means.csv`: any row whose `word_column` is `word_ukrainian` names a norming dataset that includes Ukrainian words. Each row is then matched to one of the six subjective categories below by keyword in its `variable` name, and the matching file is loaded and averaged by word. Rather than collapsing multiple sources for the same category into one averaged number, each source keeps its own column named `{category}_{file}` (e.g. `aoa_Person1986`) so it's traceable which dataset a value came from -- this also means the same category can have several columns when more than one source is available. As of now no rows match Ukrainian, so every category below comes back with no columns at all until we add our own collected norms.

```{r}
labData <- rio::import("../lab_variables_target_means.csv") %>%
  filter(word_column == "word_ukrainian")

# where the underlying norming datasets live
datasets_path <- "/Users/erinbuchanan/GitHub/Research/2_projects/SPAML/semanticprimeR/datasets/completed/"

# pull one variable column from one source file, averaged by word
get_subjective_source <- function(file, word_column, variable) {
  path <- paste0(datasets_path, file)
  if (!file.exists(path)) return(NULL)

  rio::import(path) %>%
    select(word = all_of(word_column), value = all_of(variable)) %>%
    filter(!is.na(word)) %>%
    mutate(value = as.numeric(value)) %>%
    group_by(word) %>%
    summarize(value = mean(value, na.rm = TRUE), .groups = "drop")
}

# one column per labData row whose `variable` matches `pattern`, named
# `{category}_{source file}` so multiple sources for the same category
# (e.g. two AOA norms) stay distinguishable instead of being averaged together
combine_subjective <- function(labData, pattern, category) {
  matches <- labData %>%
    filter(grepl(pattern, variable, ignore.case = TRUE))

  if (nrow(matches) == 0) {
    return(tibble(word = character()))
  }

  labels <- make.unique(tools::file_path_sans_ext(matches$file))

  sources <- purrr::pmap(matches, function(file, word_column, variable) {
    get_subjective_source(file, word_column, variable)
  })
  names(sources) <- labels
  sources <- purrr::compact(sources)

  if (length(sources) == 0) {
    return(tibble(word = character()))
  }

  purrr::imap(sources, function(d, label) {
    rename(d, !!paste0(category, "_", label) := value)
  }) %>%
    purrr::reduce(full_join, by = "word")
}
```

### AOA

```{r}
DF <- DF %>%
  left_join(combine_subjective(labData, "aoa", "aoa"), by = "word")
```

### Imageability

```{r}
DF <- DF %>%
  left_join(combine_subjective(labData, "image", "image"), by = "word")
```

### Concrete

```{r}
DF <- DF %>%
  left_join(combine_subjective(labData, "concrete", "concrete"), by = "word")
```

### Valence

```{r}
DF <- DF %>%
  left_join(combine_subjective(labData, "valence", "valence"), by = "word")
```

### Arousal

```{r}
DF <- DF %>%
  left_join(combine_subjective(labData, "arousal", "arousal"), by = "word")
```

### Familiar

```{r}
DF <- DF %>%
  left_join(combine_subjective(labData, "familiar", "familiar"), by = "word")
```

## Similarity Statistics

## Priming

### Human Prime

```{r}
# not ready yet 
```

### BERT Priming

```{r}
# not ready yet 
```

## Embeddings

Each pair is dropped into template sentences, and `get_embeddings()`/`embed_dataframe()` (from `functions.R`) pull a context-free (static) embedding for the target plus a contextual embedding of the target as it appears in each sentence. The model is a single variable below so different GPT-2-family checkpoints can be swapped in while we're still testing this out -- `embed_dataframe()` assumes a GPT-2-style architecture (it reaches into `model$transformer$wte`), so any replacement needs to expose that same structure (e.g. other `AutoModelForCausalLM`-loadable GPT-2 variants, including multilingual ones like `sberbank-ai/mGPT`).

```{r}
# swap the checkpoint here -- must be a GPT-2-architecture causal LM
embed_model_name <- "openai-community/gpt2"

reticulate::py_require(c("transformers", "torch"))
transformers <- reticulate::import("transformers")
torch <- reticulate::import("torch")

hf <- (function(model_name) {
  tokzr <- transformers$AutoTokenizer$from_pretrained(model_name)
  model <- transformers$AutoModelForCausalLM$from_pretrained(model_name)
  model$eval()
  list(tokzr = tokzr, model = model, name = model_name)
})(embed_model_name)

# target_word_unique carries a make.unique() suffix (e.g. "слово.1") for the
# handful of targets that repeat across the 1,000 pairs -- kept as-is here
# since it's what goes into the sentences and what embed_dataframe indexes
# on; `word` (suffix stripped) is what's used later to join back onto DF
llm_embed <- rio::import("../../01-Translation/03_match_stimuli/matched_stimuli/uk_trial_unique.csv") %>%
  mutate(
    word = sub("\\.[0-9]+$", "", target_word_unique),
    sentence_related = paste0("Дано слово ", cue_word_related, ", наступне слово - ", target_word_unique),
    sentence_unrelated = paste0("Дано слово ", cue_word_unrelated, ", наступне слово - ", target_word_unique)
  )

embedded <- embed_dataframe(
  llm_embed,
  tokzr = hf$tokzr,
  model = hf$model,
  layer = NULL,          # NULL = last hidden layer
  occurrence = "last",   # which occurrence of the target to use if it repeats in a sentence
  word_col = "target_word_unique",
  sent_rel_col = "sentence_related",
  sent_unrel_col = "sentence_unrelated",
  quiet = FALSE
)

# one row per pair (all 1,000 kept): static + contextual-in-related +
# contextual-in-unrelated vectors, written out on their own so we can decide
# what to do with the raw vectors later
embeddings_DF <- bind_cols(
  cue_related = llm_embed$cue_word_related,
  cue_unrelated = llm_embed$cue_word_unrelated,
  target = llm_embed$target_word_unique,
  word = llm_embed$word,
  as.data.frame(embedded$static)            %>% rename_with(~paste0("static_", .x)),
  as.data.frame(embedded$context_related)   %>% rename_with(~paste0("context_related_", .x)),
  as.data.frame(embedded$context_unrelated) %>% rename_with(~paste0("context_unrelated_", .x))
)

rio::export(embeddings_DF, "uk_embeddings.csv.gz")
```

### Cue-Target Cosine Similarity

For each pair, the cosine similarity between the target's contextual embedding in the related sentence and the unrelated sentence captures how much a related vs. unrelated prime shifts the model's representation of the target. `DF` has one row per word (not per pair), and a handful of targets show up in more than one pair, so those get averaged before the single `embedding_cosine` column is joined in.

```{r}
cosine_sim <- function(a, b) {
  if (anyNA(a) || anyNA(b)) return(NA_real_)
  sum(a * b) / (sqrt(sum(a^2)) * sqrt(sum(b^2)))
}

embedding_cosine_DF <- tibble(
  word = llm_embed$word,
  embedding_cosine = vapply(
    seq_len(nrow(llm_embed)),
    function(i) cosine_sim(embedded$context_related[i, ], embedded$context_unrelated[i, ]),
    numeric(1)
  )
) %>%
  group_by(word) %>%
  summarize(embedding_cosine = mean(embedding_cosine, na.rm = TRUE), .groups = "drop")

DF <- DF %>%
  left_join(embedding_cosine_DF, by = "word")
```

## Output Variable Match

One TRUE/FALSE column per subjective category: TRUE means no source covered that word for that category yet (still needs norming), FALSE means at least one `{category}_*` source already has a value. This drives what goes out for collection in `03-Tasks` (see `02-Stimuli/uk/{category}/{category}_list_*.csv`) -- it's a plain CSV, so it's also fine to hand-edit if a word's status needs correcting outside this pipeline.

```{r}
# TRUE if every {prefix}* column is NA for that row (or there are no such
# columns at all, e.g. no Ukrainian sources exist yet -- then everyone is TRUE)
category_missing <- function(df, prefix) {
  cols <- df %>% select(starts_with(prefix)) %>% names()
  if (length(cols) == 0) return(rep(TRUE, nrow(df)))
  apply(df[cols], 1, function(row) all(is.na(row)))
}

DF_var_match <- DF %>%
  transmute(
    word,
    aoa = category_missing(DF, "aoa_"),
    image = category_missing(DF, "image_"),
    concrete = category_missing(DF, "concrete_"),
    valence = category_missing(DF, "valence_"),
    arousal = category_missing(DF, "arousal_"),
    familiar = category_missing(DF, "familiar_")
  )

rio::export(DF_var_match, "uk_variables_normed.csv", row.names = F)
```