---
title: "German Data Combination"
author: "Erin M. Buchanan - Addie Clark"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goals

First, the lexical level variables for each item pair (prime and target frequency, etc.) will be included in the regression equation (see Goal 1 description). Next, the subjective level variables for each item pair will be added to the equation, followed by the similarity statistics. Last, the LLM embeddings for each target will be included in the regression equation.

## Libraries

```{r}
library(dplyr)
library(semanticprimeR)
library(rio)
```

## Item Data

```{r}
data("primeData")
# filter to just german
primeData <- primeData %>% 
  filter(language == "de") %>% 
  filter(type == "item_data")

# only need this line if you don't have the dataset yet 
#DF <- import_prime("de_item_data.csv")
DF <- import("item_data/de/de_item_data.csv") %>% 
  filter(class == "word") %>% 
  select(word)
```


## Lexical Data

frequency open sub
word length

1) linguistic information including length, frequency, orthographic neighborhood, bigram frequency, orthographic and phonographic Levenshtein distance, and semantic diversity 

## Subjective Data

```{r}
data("labData")
labData <- labData %>% 
  filter(language == "German" | language == "Multiple") %>% 
  filter(type1 == "Words" | type1 == "Word Pairs")
```

### AOA 

- here take a note if they say which version 
- mostly want the subjective ones

- @Birchenough2017
  - Range = ... 
  - Coverage =  195
  
 - @Russell1970
  - Range = ... 
  - Coverage =  231 


```{r}
aoaData <- labData %>% 
  filter(aoa == 1)

#Birchenough2017 <- import_lab("Birchenough2017")
Birchenough2017 <- import("lab_data/Birchenough2017.csv")
Birchenough2017$word_german <- tolower(Birchenough2017$word_german)
#Russell1970 <- import_lab("Russell1970")
Russell1970 <- import("lab_data/Russell1970.csv")


# join together 
aoaDF <- DF %>% 
  left_join(Birchenough2017 %>% 
              select(word_german, aoa_M),
            by = c("word" = "word_german")) %>% 
  dplyr::rename(Birchenough2017_M = aoa_M) %>% 
  left_join(Russell1970 %>% 
              select(word_german, aoa_M),
            by = c("word" = "word_german")) %>% 
  dplyr::rename(Russell1970_M = aoa_M) 


# coverage
nrow(aoaDF) - sum(is.na(aoaDF$Birchenough2017_M))  
nrow(aoaDF) - sum(is.na(aoaDF$Russell1970_M))  
```

### Imagine

- @Gruhn2008a
  - Range = ... 
  - Coverage = 41

- @Schmidtke2014
  - Range = ... 
  - Coverage = 384

```{r}
imageData <- labData %>% 
  filter(imagine == 1) 

#Gruhn2008a <- import_lab("Gruhn2008a")
Gruhn2008a <- import("lab_data/Gruhn2008a.csv")
#Schmidtke2014 <- import_lab("Schmidtke2014")
Schmidtke2014 <- import("lab_data/Schmidtke2014.csv")


# join together 
imageDF <- DF %>% 
  left_join(Gruhn2008a %>% 
              select(word_german, imagine_M),
            by = c("word" = "word_german")) %>% 
  dplyr::rename(Gruhn2008a_M = imagine_M) %>% 
  left_join(Schmidtke2014 %>% 
              select(word_german, imagine_M),
            by = c("word" = "word_german")) %>% 
  dplyr::rename(Schmidtke2014_M = imagine_M) 

# coverage
nrow(imageDF) - sum(is.na(imageDF$Gruhn2008a_M))
nrow(imageDF) - sum(is.na(imageDF$Schmidtke2014_M))

```

### Concrete

- @Kanske2010  
  - Range = ... 
  - Coverage =  261

```{r}
concreteData <- labData %>% 
  filter(concrete == 1)

#Kanske2010 <- import_lab("Kanske2010")
Kanske2010 <- import("lab_data/Kanske2010.csv")
Kanske2010$word_german <- tolower(Kanske2010$word_german)

# join together 
concreteDF <- DF %>% 
  left_join(Kanske2010 %>% 
              select(word_german, concrete_M),
            by = c("word" = "word_german")) %>% 
  dplyr::rename(Kanske2010_M = concrete_M) 

# coverage
nrow(concreteData) - sum(is.na(concreteDF$Kanske2010_M))

```



### Valence

- @Kanske2010: 
  - Range = 
  - Coverage = 280

- @Schauenburg2015: 
  - Range = 
  - Coverage = 177

- @Schmidtke2014: 
  - Range = 
  - Coverage = 384

```{r}
valData <- labData %>% 
  filter(valence == 1)

#Kanske2010 <- import_lab("Kanske2010")
Kanske2010 <- import("lab_data/Kanske2010.csv")
Kanske2010$word_german <- tolower(Kanske2010$word_german)
#Schauenburg2015 <- import_lab("Schauenburg2015")
Schauenburg2015 <- import("lab_data/Schauenburg2015.csv")
Schauenburg2015$word_german <- tolower(Schauenburg2015$word_german)
#Schmidtke2014 <- import_lab("Schmidtke2014")
Schmidtke2014 <- import("lab_data/Schmidtke2014.csv")

# join together 
valDF <- DF %>% 
  left_join(Kanske2010 %>% 
              select(word_german, valence_M),
            by = c("word" = "word_german")) %>% 
  dplyr::rename(Kanske2010_M = valence_M) %>% 
  left_join(Schauenburg2015 %>% 
              select(word_german, valence_M),
            by = c("word" = "word_german")) %>% 
  dplyr::rename(Schauenburg2015_M = valence_M) %>% 
  left_join(Schmidtke2014 %>% 
              select(word_german, valence_M),
            by = c("word" = "word_german")) %>% 
  dplyr::rename(Schmidtke2014_M = valence_M) 




# coverage
nrow(valDF) - sum(is.na(valDF$Kanske2010_M))
nrow(valDF) - sum(is.na(valDF$Schauenburg2015_M))
nrow(valDF) - sum(is.na(valDF$Schmidtke2014_M))

```

### Arousal

- @Kanske2010: 
  - Range = 
  - Coverage = 280

- @Schauenburg2015: 
  - Range = 
  - Coverage = 177

- @Schmidtke2014: 
  - Range = 
  - Coverage = 384 

```{r}
arouData <- labData %>% 
  filter(arousal == 1)

#Kanske2010 <- import_lab("Kanske2010")
Kanske2010 <- import("lab_data/Kanske2010.csv")
Kanske2010$word_german <- tolower(Kanske2010$word_german)
#Schauenburg2015 <- import_lab("Schauenburg2015")
Schauenburg2015 <- import("lab_data/Schauenburg2015.csv")
Schauenburg2015$word_german <- tolower(Schauenburg2015$word_german)
#Schmidtke2014 <- import_lab("Schmidtke2014")
Schmidtke2014 <- import("lab_data/Schmidtke2014.csv")

# join together 
arouDF <- DF %>% 
  left_join(Kanske2010 %>% 
              select(word_german, arousal_M),
            by = c("word" = "word_german")) %>% 
  dplyr::rename(Kanske2010_M = arousal_M) %>% 
  left_join(Schauenburg2015 %>% 
              select(word_german, arousal_M),
            by = c("word" = "word_german")) %>% 
  dplyr::rename(Schauenburg2015_M = arousal_M) %>% 
  left_join(Schmidtke2014 %>% 
              select(word_german, arousal_M_ANEW),
            by = c("word" = "word_german")) %>% 
  dplyr::rename(Schmidtke2014_M = arousal_M_ANEW)


# coverage
nrow(arouDF) - sum(is.na(arouDF$Kanske2010_M))
nrow(arouDF) - sum(is.na(arouDF$Schauenburg2015_M))
nrow(arouDF) - sum(is.na(arouDF$Schmidtke2014_M))

```



  
### Familiar

- @Guasch2016  
  - Range = ... 
  - Coverage =  403

- @Izura2005  
  - Range = ... 
  - Coverage =  134
  
- @MorenoMartinez2014  
  - Range = ... 
  - Coverage =  147  

```{r}
familiarData <- labData %>% 
  filter(familiar == 1)

## zero coverage for german familiar :( 
```


## Similarity Statistics

## Priming

### Human Prime

```{r}
data("primeData")
# filter to just spanish
primeData <- primeData %>% 
  filter(language == "de") 

#de_prime <- import_prime("de_prime_summary.csv")
de_prime <- import("priming_data/de/de_prime_summary.csv")

de_matched <- import_prime("de_trial_unique.csv")
```

### BERT Priming

## Embeddings

## Combine

```{r}

```