---
title: "English Data Combination"
author: "Erin M. Buchanan"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(dplyr)
library(semanticprimeR)
library(rio)
```

## Item Data

```{r}
data("primeData")
# filter to just english
primeData <- primeData %>% 
  filter(language == "en") %>% 
  filter(type == "item_data")

# only need this line if you don't have the dataset yet 
#DF <- import_prime("en_item_data.csv")
DF <- import("item_data/en/en_item_data.csv") %>% 
  filter(class == "word") %>% 
  select(word)
```

## Datasets

```{r}
data("labData")
labData <- labData %>% 
  filter(language == "English" | language == "British English" | language == "Multiple") %>% 
  filter(type1 == "Words" | type1 == "Word Pairs")
```

## AOA 

- here take a note if they say which version 
- mostly want the subjective ones

- @Bestgen2012
- @Clark2004
- @Juhasz2015
  - Range = ... 
  - Coverage =   

- @Morrow2005  
  - Range = ... 
  - Coverage =    
  
```{r}
aoaData <- labData %>% 
  filter(aoa == 1)

aoaData

#Kuperman2012
#Brysbaert2017
```

## Imagine

- @Elsherif2020
  - Range = ... 
  - Coverage = 4
  
- @Altarriba1999
  - Range = ... 
  - Coverage = 154
  
- @Bestgen2012
  - Range = ... 
  - Coverage_M = 525
  - Coverage_LSA_M = 1889

- @Chiarello1999
  - Range = ... 
  - Coverage = 265 

- @Clark2004
  - Range = ... 
  - Coverage = 279 
  
- @Cohen-Shikora2013
  - Range = ... 
  - Coverage = 343  
 
- @Cortese2004
  - Range = ... 
  - Coverage = 562     
  
- @Janschewitz2008
  - Range = ... 
  - Coverage = 405     
  
- @Juhasz2015
  - Range = ... 
  - Coverage =  16    
  
- @Morrow2005  
  - Range = ... 
  - Coverage_younger =  124
  - Coverage_older =  124
  
  
  Bestgen2012


```{r}
imageData <- labData %>% 
  filter(imagine == 1) 

#Elsherif2020 <- import_lab("Elsherif2020")
Elsherif2020 <- import("lab_data/Elsherif2020.csv")
#Altarriba1999 <- import_lab("Altarriba1999")
Altarriba1999 <- import("lab_data/Altarriba1999.csv")
#Bestgen2012 <- import_lab("Bestgen2012")
Bestgen2012 <- import("lab_data/Bestgen2012.csv") 
#Chiarello1999 <- import_lab("Chiarello1999")
Chiarello1999 <- import("lab_data/Chiarello1999.csv")
#Clark2004 <- import_lab("Clark2004")
Clark2004 <- import("lab_data/Clark2004.csv")
Clark2004$word_english <- tolower(Clark2004$word_english)
#Clark2004 <- import_lab("Clark2004")
Clark2004 <- import("lab_data/Clark2004.csv")
#Cohen_Shikora2013 <- import_lab("Cohen-Shikora2013")
Cohen_Shikora2013 <- import("lab_data/Cohen-Shikora2013.csv")
#Cortese2004 <- import_lab("Cortese2004")
Cortese2004 <- import("lab_data/Cortese2004.csv")
#Janschewitz2008 <- import_lab("Janschewitz2008")
Janschewitz2008 <- import("lab_data/Janschewitz2008.csv")
#Juhasz2013 <- import_lab("Juhasz2013")
#Juhasz2013 <- import("lab_data/Juhasz2013.csv")
#Juhasz2015 <- import_lab("Juhasz2015")
Juhasz2015 <- import("lab_data/Juhasz2015.csv")
#Morrow2005 <- import_lab("Morrow2005")
Morrow2005 <- import("lab_data/Morrow2005.csv")

# join together 
imageDF <- DF %>% 
  left_join(Elsherif2020 %>% 
              select(word_english, imagine_M_British, imagine_M_American), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Elsherif2020_M_British = imagine_M_British, 
                Elsherif2020_M_American = imagine_M_American) %>%
  left_join(Altarriba1999 %>% 
              select(word_english, imagine_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Altarriba1999_M = imagine_M) %>%
  left_join(Bestgen2012 %>% 
              select(word_english, imagine_norms_M, imagine_LSA_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Bestgen2012_M = imagine_norms_M,
                Bestgen2012_LSA_M = imagine_LSA_M) %>% 
  left_join(Chiarello1999 %>% 
              select(word_english, imagine_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Chiarello1999_M = imagine_M) %>% 
  left_join(Clark2004 %>% 
              select(word_english, imagine_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Clark2004_M = imagine_M) %>% 
  left_join(Cohen_Shikora2013 %>% 
              select(word_english, imagine_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Cohen_Shikora2013_M = imagine_M) %>% 
  left_join(Cortese2004 %>% 
              select(word_english, imagine_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Cortese2004_M = imagine_M) %>% 
  left_join(Janschewitz2008 %>% 
              select(word_english, imagine_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Janschewitz2008_M = imagine_M) %>% 
  left_join(Juhasz2015 %>% 
              select(word_english, imagine_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Juhasz2015_M = imagine_M) %>% 
  left_join(Morrow2005 %>% 
              select(word_english, imagine_M_younger, imagine_M_older), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Morrow2005_M_younger = imagine_M_younger,
                Morrow2005_M_older = imagine_M_older)                       


nrow(imageDF)

# coverage
nrow(imageDF) - sum(is.na(imageDF$Morrow2005))

```

## Concrete

- @Altarriba1999
- @Bestgen2012
- @Clark2004
- @Altarriba1999_M  
  - Range = ... 
  - Coverage =  134
- @Bestgen2012 
  - Range = ... 
  - Coverage =  545  
- @Brysbaert2014
  - Range = ...  
  - Coverage =  1952  
- @Eilola2010
  - Range = ...  
  - Coverage = 92 
- @Pexman2017
  - Range = ...  
  - Coverage = 613

```{r}
concreteData <- labData %>% 
  filter(concrete == 1)

#Altarriba1999 <- import_lab("Altarriba1999")
Altarriba1999 <- import("lab_data/Altarriba1999.csv")
#Bestgen2012 <- import_lab("Bestgen2012")
Bestgen2012 <- import("lab_data/Bestgen2012.csv")
#Brysbaert2014 <- import_lab("Brysbaert2014")
Brysbaert2014 <- import("lab_data/Brysbaert2014.csv") 
#Eilola2010 <- import_lab("Eilola2010")
Eilola2010 <- import("lab_data/Eilola2010.csv") 
#Pexman2017 <- import_lab("Pexman2017")
Pexman2017 <- import("lab_data/Pexman2017.csv") 


# join together 
concreteDF <- DF %>% 
  left_join(Altarriba1999 %>% 
              select(word_english, concrete_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Altarriba1999_M = concrete_M) %>% 
  left_join(Bestgen2012 %>% 
              select(word_english, concrete_norms_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Bestgen2012_M = concrete_norms_M) %>% 
  left_join(Brysbaert2014 %>% 
              select(word_english, concrete_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Brysbaert2014_M = concrete_M) %>% 
  left_join(Eilola2010 %>% 
              select(word_english, concrete_M_english), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Eilola2010_M = concrete_M_english) %>% 
  left_join(Pexman2017 %>% 
              select(word_english, concrete_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Pexman2017_M = concrete_M)


# coverage
nrow(concreteData) - sum(is.na(concreteDF$Altarriba1999_M))
nrow(concreteData) - sum(is.na(concreteDF$Bestgen2012_M))
nrow(concreteData) - sum(is.na(concreteDF$Brysbaert2014_M))
nrow(concreteData) - sum(is.na(concreteDF$Eilola2010_M))
nrow(concreteData) - sum(is.na(concreteDF$Pexman2017_M))

```



## Valence

- @Warriner2013: 
  - Range = 
  - Coverage = 1853/2000
  
- @Bestgen2012
  - Range = 
  - Coverage = 409/2000

- @Eilola2010 
  - Range = ... 
  - Coverage =  112

- @Ferstl2011 
  - Range = ... 
  - Coverage =  5  

- @Janschewitz2008
  - Range = ... 
  - Coverage =  426  
  
- @Leveau2012 
  - Range = ... 
  - Coverage =  2284  

- @Warriner2013
  - Range = ... 
  - Coverage =  

```{r}
valData <- labData %>% 
  filter(valence == 1)

#Warriner2013 <- import_lab("Warriner2013")
Warriner2013 <- import("lab_data/Warriner2013.csv")
#Bestgen2012 <- import_lab("Bestgen2012")
Bestgen2012 <- import("lab_data/Bestgen2012.csv")
#Eilola2010 <- import_lab("Eilola2010")
Eilola2010 <- import("lab_data/Eilola2010.csv")
#Ferstl2011 <- import_lab("Ferstl2011")
Ferstl2011 <- import("lab_data/Ferstl2011.csv")
#Janschewitz2008 <- import_lab("Janschewitz2008")
Janschewitz2008 <- import("lab_data/Janschewitz2008.csv")

# join together 
valDF <- DF %>% 
  left_join(Warriner2013 %>% 
              select(word_english, valence_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Warriner2013_M = valence_M) %>% 
  left_join(Bestgen2012 %>% 
              select(word_english, valence_norms_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Bestgen2012_M = valence_norms_M) %>% 
  left_join(Eilola2010 %>% 
              select(word_english, valence_M_english), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Eilola2010_M = valence_M_english) %>% 
  left_join(Ferstl2011 %>% 
              select(word_english, valence_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Ferstl2011_M = valence_M) %>% 
  left_join(Janschewitz2008 %>% 
              select(word_english, valence_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Janschewitz2008_M = valence_M) 


# coverage
nrow(valDF) - sum(is.na(valDF$Warriner2013_M))
nrow(valDF) - sum(is.na(valDF$Bestgen2012_M))
nrow(valDF) - sum(is.na(valDF$Eilola2010_M))
nrow(valDF) - sum(is.na(valDF$Ferstl2011_M))
nrow(valDF) - sum(is.na(valDF$Janschewitz2008_M))
```

## Arousal

Bestgen2012

- @Janschewitz2008
  - Range = ... 
  - Coverage =  
  
## Familiar

Elsherif2020
Chiarello1999
Eilola2010
@Clark2004
- @Janschewitz2008
  - Range = ... 
  - Coverage =  

- @Juhasz2015
  - Range = ... 
  - Coverage =   

- @Morrow2005  
  - Range = ... 
  - Coverage =  
  
## Prime

## Combine

```{r}

```