---
title: "English Data Combination"
author: "Erin M. Buchanan - Addie Clark"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goals

First, the lexical level variables for each item pair (prime and target frequency, etc.) will be included in the regression equation (see Goal 1 description). Next, the subjective level variables for each item pair will be added to the equation, followed by the similarity statistics. Last, the LLM embeddings for each target will be included in the regression equation.

## Libraries

```{r}
library(dplyr)
library(semanticprimeR)
library(reticulate)
library(rio)
source("functions.R")
```

## Item Data

```{r}
data("primeData")
# filter to just english
primeData <- primeData %>% 
  filter(language == "en") %>% 
  filter(type == "item_data")

# only need this line if you don't have the dataset yet 
# import_prime("en_item_data.csv")
DF <- rio::import("item_data/en/en_item_data.csv") %>% 
  filter(class == "word") %>% 
  select(word)
```

## Lexical Data

```{r}
# length
DF$length <- nchar(DF$word)

# frequency processed with phonemes
subs_DF <- rio::import("subs_count/en/subs_DF_phono.csv") %>% 
  unique()

DF <- DF %>% 
  left_join(subs_DF, by = c("word" = "unigram"))

# orthographic neighborhood
DF <- calc_neighbors(DF, subs_DF)

# bigram frequency
DF <- add_bigram_frequency(DF, subs_DF, weight = "unigram_freq")

# orthographic Levenshtein
DF <- add_orthographic_levenshtein(DF, subs_DF, k = 20, max_len_diff = 3)

# phonographic Levenshtein
DF <- add_phonographic_levenshtein(DF, k = 20, max_len_diff = 3)

# semantic diversity
DF <- DF %>% 
  left_join(
    rio::import("semdiv_data/en/en_semantic_diversity.csv") %>% 
      select(-V1),
    by = c("word" = "term")
  )

# check out the NAs
```

## Subjective Data

```{r}
data("labData")
labData <- labData %>% 
  filter(language == "English" | language == "British English" | language == "Multiple") %>% 
  filter(type1 == "Words" | type1 == "Word Pairs")
```

### AOA 

- here take a note if they say which version 
- mostly want the subjective ones

- @Clark2004
  - Range = ... 
  - Coverage =  300

- @Cortese2008
  - Range = ... 
  - Coverage =  582

- @Elsherif2020
  - Range = ... 
  - Coverage =  4  
  
- @Juhasz2015
  - Range = ... 
  - Coverage =  14 

- @Khanna2011_1
  - Range = ... 
  - Coverage =  1269

- @Khanna2011_2_dominate
  - Range = ... 
  - Coverage =  375
  
- @Khanna2011_2_subordinate
  - Range = ... 
  - Coverage =  375  

- @Morrow2005_older  
  - Range = ... 
  - Coverage =  162 

- @Morrow2005_younger  
  - Range = ... 
  - Coverage =  162 
  
- @Schock2012 
  - Range = ... 
  - Coverage =  798   
  
```{r}
aoaData <- labData %>% 
  filter(aoa == 1)

#Clark2004 <- import_lab("Clark2004")
Clark2004 <- import("lab_data/Clark2004.csv")
Clark2004$word_english <- tolower(Clark2004$word_english)
#Cortese2008 <- import_lab("Cortese2008")
Cortese2008 <- import("lab_data/Cortese2008.csv")
#Elsherif2020 <- import_lab("Elsherif2020")
Elsherif2020 <- import("lab_data/Elsherif2020.csv")
#Juhasz2015 <- import_lab("Juhasz2015")
Juhasz2015 <- import("lab_data/Juhasz2015.csv")
#Khanna2011_1 <- import_lab("Khanna2011_1")
Khanna2011_1 <- import("lab_data/Khanna2011_1.csv")
#Khanna2011_2 <- import_lab("Khanna2011_2")
Khanna2011_2 <- import("lab_data/Khanna2011_2.csv")
#Morrow2005 <- import_lab("Morrow2005")
Morrow2005 <- import("lab_data/Morrow2005.csv")
#Schock2012 <- import_lab("Schock2012")
Schock2012 <- import("lab_data/Schock2012.csv")

# join together 
aoaDF <- DF %>% 
  left_join(Clark2004 %>% 
              select(word_english, aoa_M),
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Clark2004_M = aoa_M) %>% 
  left_join(Cortese2008 %>% 
              select(word_english, aoa_s_M),
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Cortese2008_M = aoa_s_M) %>% 
  left_join(Elsherif2020 %>% 
              select(word_english, aoa_M_log),
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Elsherif2020_M = aoa_M_log) %>% 
  left_join(Juhasz2015 %>% 
              select(word_english, aoa_s_M),
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Juhasz2015_M = aoa_s_M) %>% 
  left_join(Khanna2011_1 %>% 
              select(word_english, aoa_M),
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Khanna2011_1_M = aoa_M) %>% 
  left_join(Khanna2011_2 %>% 
              select(word_english, aoa_M_dominate, aoa_M_subordinate), #I don't think subordiante is necessary here but figured i'd include just in case
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Khanna2011_2_M_dominate = aoa_M_dominate, 
                Khanna2011_2_M_subordinate = aoa_M_subordinate) %>% 
  left_join(Morrow2005 %>% 
              select(word_english, aoa_M_older, aoa_M_younger), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Morrow2005_M_older = aoa_M_older, 
                Morrow2005_M_younger = aoa_M_younger) %>% 
  left_join(Schock2012 %>% 
              select(word_english, aoa_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Schock2012_M = aoa_M)

nrow(aoaDF) - sum(is.na(aoaDF$Clark2004_M)) 
nrow(aoaDF) - sum(is.na(aoaDF$Cortese2008_M)) 
nrow(aoaDF) - sum(is.na(aoaDF$Elsherif2020_M)) 
nrow(aoaDF) - sum(is.na(aoaDF$Juhasz2015_M)) 
nrow(aoaDF) - sum(is.na(aoaDF$Khanna2011_1_M)) 
nrow(aoaDF) - sum(is.na(aoaDF$Khanna2011_2_M_dominate)) 
nrow(aoaDF) - sum(is.na(aoaDF$Khanna2011_2_M_subordinate)) 
nrow(aoaDF) - sum(is.na(aoaDF$Morrow2005_M_older)) 
nrow(aoaDF) - sum(is.na(aoaDF$Morrow2005_M_younger)) 
nrow(aoaDF) - sum(is.na(aoaDF$Schock2012_M)) 
```

### Imagine

- @Elsherif2020
  - Range = ... 
  - Coverage = 4
  
- @Altarriba1999
  - Range = ... 
  - Coverage = 154
  
- @Bestgen2012
  - Range = ... 
  - Coverage_M = 525
  - Coverage_LSA_M = 1889

- @Chiarello1999
  - Range = ... 
  - Coverage = 265 

- @Clark2004
  - Range = ... 
  - Coverage = 279 
  
- @Cohen-Shikora2013
  - Range = ... 
  - Coverage = 343  
 
- @Cortese2004
  - Range = ... 
  - Coverage = 562     
  
- @Janschewitz2008
  - Range = ... 
  - Coverage = 405     
  
- @Juhasz2015
  - Range = ... 
  - Coverage =  16    
  
- @Morrow2005  
  - Range = ... 
  - Coverage_younger =  124
  - Coverage_older =  124
  
  
  Bestgen2012


```{r}
imageData <- labData %>% 
  filter(imagine == 1) 

#Elsherif2020 <- import_lab("Elsherif2020")
Elsherif2020 <- import("lab_data/Elsherif2020.csv")
#Altarriba1999 <- import_lab("Altarriba1999")
Altarriba1999 <- import("lab_data/Altarriba1999.csv")
#Bestgen2012 <- import_lab("Bestgen2012")
Bestgen2012 <- import("lab_data/Bestgen2012.csv") 
#Chiarello1999 <- import_lab("Chiarello1999")
Chiarello1999 <- import("lab_data/Chiarello1999.csv")
#Clark2004 <- import_lab("Clark2004")
Clark2004$word_english <- tolower(Clark2004$word_english)
#Clark2004 <- import_lab("Clark2004")
Clark2004 <- import("lab_data/Clark2004.csv")
#Cohen_Shikora2013 <- import_lab("Cohen-Shikora2013")
Cohen_Shikora2013 <- import("lab_data/Cohen-Shikora2013.csv")
#Cortese2004 <- import_lab("Cortese2004")
Cortese2004 <- import("lab_data/Cortese2004.csv")
#Janschewitz2008 <- import_lab("Janschewitz2008")
Janschewitz2008 <- import("lab_data/Janschewitz2008.csv")
#Juhasz2013 <- import_lab("Juhasz2013")
Juhasz2013 <- import("lab_data/Juhasz2013.csv")
#Juhasz2015 <- import_lab("Juhasz2015")
Juhasz2015 <- import("lab_data/Juhasz2015.csv")
#Morrow2005 <- import_lab("Morrow2005")
Morrow2005 <- import("lab_data/Morrow2005.csv")

# join together 
imageDF <- DF %>% 
  left_join(Elsherif2020 %>% 
              select(word_english, imagine_M_British, imagine_M_American), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Elsherif2020_M_British = imagine_M_British, 
                Elsherif2020_M_American = imagine_M_American) %>%
  left_join(Altarriba1999 %>% 
              select(word_english, imagine_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Altarriba1999_M = imagine_M) %>%
  left_join(Bestgen2012 %>% 
              select(word_english, imagine_norms_M, imagine_LSA_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Bestgen2012_M = imagine_norms_M,
                Bestgen2012_LSA_M = imagine_LSA_M) %>% 
  left_join(Chiarello1999 %>% 
              select(word_english, imagine_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Chiarello1999_M = imagine_M) %>% 
  left_join(Clark2004 %>% 
              select(word_english, imagine_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Clark2004_M = imagine_M) %>% 
  left_join(Cohen_Shikora2013 %>% 
              select(word_english, imagine_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Cohen_Shikora2013_M = imagine_M) %>% 
  left_join(Cortese2004 %>% 
              select(word_english, imagine_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Cortese2004_M = imagine_M) %>% 
  left_join(Janschewitz2008 %>% 
              select(word_english, imagine_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Janschewitz2008_M = imagine_M) %>% 
  left_join(Juhasz2015 %>% 
              select(word_english, imagine_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Juhasz2015_M = imagine_M) %>% 
  left_join(Morrow2005 %>% 
              select(word_english, imagine_M_younger, imagine_M_older), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Morrow2005_M_younger = imagine_M_younger,
                Morrow2005_M_older = imagine_M_older)                       


# coverage
nrow(imageDF) - sum(is.na(imageDF$Elsherif2020_M_British))
nrow(imageDF) - sum(is.na(imageDF$Elsherif2020_M_American))
nrow(imageDF) - sum(is.na(imageDF$Altarriba1999_M))
nrow(imageDF) - sum(is.na(imageDF$Bestgen2012_M))
nrow(imageDF) - sum(is.na(imageDF$Bestgen2012_LSA_M))
nrow(imageDF) - sum(is.na(imageDF$Chiarello1999_M))
nrow(imageDF) - sum(is.na(imageDF$Clark2004_M))
nrow(imageDF) - sum(is.na(imageDF$Cohen_Shikora2013_M))
nrow(imageDF) - sum(is.na(imageDF$Cortese2004_M))
nrow(imageDF) - sum(is.na(imageDF$Janschewitz2008_M))
nrow(imageDF) - sum(is.na(imageDF$Juhasz2015_M))
nrow(imageDF) - sum(is.na(imageDF$Morrow2005_M_older))
nrow(imageDF) - sum(is.na(imageDF$Morrow2005_M_younger))

```

### Concrete

- @Altarriba1999
- @Bestgen2012
- @Clark2004
- @Altarriba1999_M  
  - Range = ... 
  - Coverage =  134
- @Bestgen2012 
  - Range = ... 
  - Coverage =  545  
- @Brysbaert2014
  - Range = ...  
  - Coverage =  1952  
- @Eilola2010
  - Range = ...  
  - Coverage = 92 
- @Pexman2017
  - Range = ...  
  - Coverage = 613

```{r}
concreteData <- labData %>% 
  filter(concrete == 1)

#Altarriba1999 <- import_lab("Altarriba1999")
Altarriba1999 <- import("lab_data/Altarriba1999.csv")
#Bestgen2012 <- import_lab("Bestgen2012")
Bestgen2012 <- import("lab_data/Bestgen2012.csv")
#Brysbaert2014 <- import_lab("Brysbaert2014")
Brysbaert2014 <- import("lab_data/Brysbaert2014.csv") 
#Eilola2010 <- import_lab("Eilola2010")
Eilola2010 <- import("lab_data/Eilola2010.csv") 
#Pexman2017 <- import_lab("Pexman2017")
Pexman2017 <- import("lab_data/Pexman2017.csv") 


# join together 
concreteDF <- DF %>% 
  left_join(Altarriba1999 %>% 
              select(word_english, concrete_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Altarriba1999_M = concrete_M) %>% 
  left_join(Bestgen2012 %>% 
              select(word_english, concrete_norms_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Bestgen2012_M = concrete_norms_M) %>% 
  left_join(Brysbaert2014 %>% 
              select(word_english, concrete_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Brysbaert2014_M = concrete_M) %>% 
  left_join(Eilola2010 %>% 
              select(word_english, concrete_M_english), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Eilola2010_M = concrete_M_english) %>% 
  left_join(Pexman2017 %>% 
              select(word_english, concrete_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Pexman2017_M = concrete_M)


# coverage
nrow(concreteData) - sum(is.na(concreteDF$Altarriba1999_M))
nrow(concreteData) - sum(is.na(concreteDF$Bestgen2012_M))
nrow(concreteData) - sum(is.na(concreteDF$Brysbaert2014_M))
nrow(concreteData) - sum(is.na(concreteDF$Eilola2010_M))
nrow(concreteData) - sum(is.na(concreteDF$Pexman2017_M))

```



### Valence

- @Warriner2013: 
  - Range = 
  - Coverage = 1853/2000
  
- @Bestgen2012
  - Range = 
  - Coverage = 409/2000

- @Eilola2010 
  - Range = ... 
  - Coverage =  112

- @Ferstl2011 
  - Range = ... 
  - Coverage =  5  

- @Janschewitz2008
  - Range = ... 
  - Coverage =  426  
  
- @Leveau2012 
  - Range = ... 
  - Coverage =  2284  

- @Warriner2013
  - Range = ... 
  - Coverage =  

```{r}
valData <- labData %>% 
  filter(valence == 1)

#Warriner2013 <- import_lab("Warriner2013")
Warriner2013 <- import("lab_data/Warriner2013.csv")
#Bestgen2012 <- import_lab("Bestgen2012")
Bestgen2012 <- import("lab_data/Bestgen2012.csv")
#Eilola2010 <- import_lab("Eilola2010")
Eilola2010 <- import("lab_data/Eilola2010.csv")
#Ferstl2011 <- import_lab("Ferstl2011")
Ferstl2011 <- import("lab_data/Ferstl2011.csv")
#Janschewitz2008 <- import_lab("Janschewitz2008")
Janschewitz2008 <- import("lab_data/Janschewitz2008.csv")

# join together 
valDF <- DF %>% 
  left_join(Warriner2013 %>% 
              select(word_english, valence_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Warriner2013_M = valence_M) %>% 
  left_join(Bestgen2012 %>% 
              select(word_english, valence_norms_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Bestgen2012_M = valence_norms_M) %>% 
  left_join(Eilola2010 %>% 
              select(word_english, valence_M_english), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Eilola2010_M = valence_M_english) %>% 
  left_join(Ferstl2011 %>% 
              select(word_english, valence_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Ferstl2011_M = valence_M) %>% 
  left_join(Janschewitz2008 %>% 
              select(word_english, valence_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Janschewitz2008_M = valence_M) 


# coverage
nrow(valDF) - sum(is.na(valDF$Warriner2013_M))
nrow(valDF) - sum(is.na(valDF$Bestgen2012_M))
nrow(valDF) - sum(is.na(valDF$Eilola2010_M))
nrow(valDF) - sum(is.na(valDF$Ferstl2011_M))
nrow(valDF) - sum(is.na(valDF$Janschewitz2008_M))
```

### Arousal

- @Bestgen2012
  - Range = ... 
  - Coverage =  389

- @Janschewitz2008
  - Range = ... 
  - Coverage =  1853

- @Warriner2013
  - Range = ... 
  - Coverage =  


```{r}
arouData <- labData %>% 
  filter(arousal == 1)

#Bestgen2012 <- import_lab("Warriner2013")
Bestgen2012 <- import("lab_data/Bestgen2012.csv")
#Janschewitz2008 <- import_lab("Janschewitz2008")
Janschewitz2008 <- import("lab_data/Janschewitz2008.csv")
#Warriner2013 <- import_lab("Warriner2013")
Warriner2013 <- import("lab_data/Warriner2013.csv")

# join together 
arouDF <- DF %>% 
  left_join(Bestgen2012 %>% 
              select(word_english, arousal_norms_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Bestgen2012_M = arousal_norms_M) %>% 
  left_join(Warriner2013 %>% 
              select(word_english, arousal_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Warriner2013_M = arousal_M) #%>% 
#  left_join(Janschewitz2008 %>% 
#              select(word_english, arousal_M), 
#            by = c("word" = "word_english")) %>% 
#  dplyr::rename(Janschewitz2008_M = arousal_M)
#> names(Janschewitz2008)
# [1] "rater"            "word_english"     "type"            
# [4] "letters_N"        "syllables_N"      "frequency_KF"    
# [7] "valence_ANEW_M"   "arousal_M"        "personal_use_M"  ## arousal_M one 
#[10] "personal_use_SD"  "familiarity_M"    "familiarity_SD"  
#[13] "offensiveness_M"  "offensiveness_SD" "tabooness_M"     
#[16] "tabooness_SD"     "valence_M"        "valence_SD"      
#[19] "arousal_M"        "arousal_SD"       "imagine_M"       ## arousal_M two 
#[22] "imagine_SD"     



# coverage
nrow(arouDF) - sum(is.na(arouDF$Bestgen2012_M))
#nrow(arouDF) - sum(is.na(arouDF$Janschewitz2008_M))
nrow(arouDF) - sum(is.na(arouDF$Warriner2013_M ))
```



  
### Familiar

Elsherif2020
Chiarello1999
Eilola2010
@Clark2004
- @Janschewitz2008
  - Range = ... 
  - Coverage =  

- @Juhasz2015
  - Range = ... 
  - Coverage =   

- @Morrow2005  
  - Range = ... 
  - Coverage =  

```{r}
familiarData <- labData %>% 
  filter(familiar == 1)

#Amsel2012 <- import_lab("Amsel2012")
Amsel2012 <- import("lab_data/Amsel2012.csv")
#Clark2004 <- import_lab("Clark2004")
Clark2004 <- import("lab_data/Clark2004.csv")
Clark2004$word_english <- tolower(Clark2004$word_english)
#Eilola2010 <- import_lab("Eilola2010")
Eilola2010 <- import("lab_data/Eilola2010.csv")
#Elsherif2020 <- import_lab("Elsherif2020")
Elsherif2020 <- import("lab_data/Elsherif2020.csv")
#Janschewitz2008 <- import_lab("Janschewitz2008")
Janschewitz2008 <- import("lab_data/Janschewitz2008.csv")
#Juhasz2015 <- import_lab("Juhasz2015")
Juhasz2015 <- import("lab_data/Juhasz2015.csv")
#Morrow2005 <- import_lab("Morrow2005")
Morrow2005 <- import("lab_data/Morrow2005.csv")

# join together 
familiarDF <- DF %>% 
  left_join(Amsel2012 %>% 
              select(word_english, familiar_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Amsel2012_M = familiar_M) %>% 
  left_join(Clark2004 %>% 
              select(word_english, familiar_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Clark2004_M = familiar_M) %>% 
  left_join(Eilola2010 %>% 
              select(word_english, familiar_M_english, familiar_M_finnish), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Eilola2010_M_english = familiar_M_english, 
                Eilola2010_M_finnish = familiar_M_finnish,) %>% 
  left_join(Elsherif2020 %>% 
              select(word_english, familiar_M_American,familiar_M_British), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Elsherif2020_M_American = familiar_M_American,
                Elsherif2020_M_British = familiar_M_British) %>% 
  left_join(Janschewitz2008 %>% 
              select(word_english, familiarity_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Janschewitz2008_M = familiarity_M) %>% 
  left_join(Juhasz2015 %>% 
              select(word_english, familiar_M), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Juhasz2015_M = familiar_M) %>% 
  left_join(Morrow2005 %>% 
              select(word_english, familiar_M_older, familiar_M_younger), 
            by = c("word" = "word_english")) %>% 
  dplyr::rename(Morrow2005_M_older = familiar_M_older,
                Morrow2005_M_younger = familiar_M_younger)  


nrow(familiarDF) - sum(is.na(familiarDF$Amsel2012_M))
nrow(familiarDF) - sum(is.na(familiarDF$Clark2004_M))
nrow(familiarDF) - sum(is.na(familiarDF$Eilola2010_M))
nrow(familiarDF) - sum(is.na(familiarDF$Elsherif2020_M))
nrow(familiarDF) - sum(is.na(familiarDF$Janschewitz2008_M))
nrow(familiarDF) - sum(is.na(familiarDF$Juhasz2015_M))
nrow(familiarDF) - sum(is.na(familiarDF$Morrow2005_M_older))
nrow(familiarDF) - sum(is.na(familiarDF$Morrow2005_M_younger))
```

## Similarity Statistics

## Priming

### Human Prime

```{r}
data("primeData")
# filter to just english
primeData <- primeData %>% 
  filter(language == "en") 

#en_prime <- import_prime("en_prime_summary.csv")
en_prime <- import("priming_data/en/en_prime_summary.csv")
en_matched <- import_prime("en_trial_unique.csv")
```

### LLM Priming

```{r}
# cue needs to come first, target always last 
llm_prime <- en_matched %>% 
  select(target_word_unique, cue_word_related, cue_word_unrelated) %>% 
  mutate(sentence_related = paste0("Given the word ", cue_word_related, ", the next word is ", target_word_unique), 
         sentence_unrelated = paste0("Given the word ", cue_word_unrelated, ", the next word is ", target_word_unique)
         )

#sentence_related = paste0("After the word", cue_word_related, ", comes the word", target_word_unique). 
#sentence_unrelated = paste0("After the word", cue_word_unrelated, ", comes the word, target_word_unique). 

#sentence_related = paste0("The pair begins with", cue_word_related, ", and continues with", target_word_unique). 
#sentence_unrelated = paste0("The pair begins with", cue_word_unrelated, ", and continues with", target_word_unique). 

#sentence_related = paste0("If the first word is", cue_word_related, ", the next word you’ll see is", target_word_unique). 
#sentence_unrelated = paste0("If the first word is", cue_word_unrelated, ", the next word you’ll see is", target_word_unique). 

transformers <- reticulate::import("transformers")
# 1) Compute last-word surprisal for each sentence and the priming delta (B − A)
res <- priming_delta(
  sentence_A = llm_prime$sentence_related,
  sentence_B = llm_prime$sentence_unrelated,
  log.p = 0.5,  # bits; use 1 for nats
  model = "openai-community/gpt2" # multilingual model like facebook 
)

# 1) Compute last-word surprisal for each sentence and the priming delta (B − A)
res2 <- priming_delta( #probably should have called this priming_delta2....
  sentence_A = llm_prime$sentence_related,
  sentence_B = llm_prime$sentence_unrelated,
  log.p = 0.5,  # bits; use 1 for nats
  model = "bigscience/bloom-560m" # multilingual model like facebook 
)

# 2) Attach the results back to your data
llm_prime <- bind_cols(
  llm_prime,
  res %>% select(
    last_word_A, surprisal_A, 
    last_word_B, surprisal_B, 
    priming_delta
  ),
  res2 %>% select(
    last_word_A, surprisal_A, 
    last_word_B, surprisal_B, 
    priming_delta #probably should have called this priming_delta2...
  )
)

llm_prime
```

```{r}
library(ggplot2)
ggplot(llm_prime, aes(priming_delta)) + 
  geom_density() + 
  geom_vline(xintercept = 0) +
  theme_classic()

ggplot(en_prime, aes(avgZ_prime)) + 
  geom_density() + 
  geom_vline(xintercept = 0) +
  theme_classic()

together <- en_prime %>% 
  select(target_word_unique, avgZ_prime) %>% 
  left_join(llm_prime %>% 
              select(target_word_unique, priming_delta))

ggplot(together, aes(x = avgZ_prime, y = priming_delta)) + 
  geom_point() +
  theme_classic()

cor(together$avgZ_prime, together$priming_delta)
```

## Embeddings

```{r}
transformers <- reticulate::import("transformers")
torch <- reticulate::import("torch")

hf <- (function(model_name = "gpt2") {
  tokzr <- transformers$AutoTokenizer$from_pretrained(model_name)
  model <- transformers$AutoModelForCausalLM$from_pretrained(model_name)
  model$eval()
  list(tokzr = tokzr, model = model, name = model_name)
})("gpt2")

batched <- embed_dataframe(
  llm_prime,
  tokzr = hf$tokzr,
  model = hf$model,
  layer = 12,          # or NULL for last; for gpt2-small last == 13th entry in hidden_states list
  occurrence = "last", # which occurrence to use if word appears multiple times
  word_col = "target_word_unique",
  sent_rel_col = "sentence_related",
  sent_unrel_col = "sentence_unrelated",
  quiet = FALSE
)

# Access results:
static_mat      <- batched$static
context_rel_mat <- batched$context_related
context_unrel_mat <- batched$context_unrelated
```
## Combine

```{r}

```