---
title: "Afrikaans Stimuli and Methods"
author: "Erin M. Buchanan & Addie Clark"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(dplyr)
library(semanticprimeR)
library(reticulate)
library(rio)
source("../functions.R")
```

# Stimuli Requirements

First, the lexical level variables for each item pair (prime and target frequency, etc.) will be included in the regression equation (see Goal 1 description). Next, the subjective level variables for each item pair will be added to the equation, followed by the similarity statistics. Last, the LLM embeddings for each target will be included in the regression equation.

## Item Data

```{r}
# load translation - this was not done in round 1
# convert to item data format
DF <- rio::import("afr_word_pairs_update.csv") %>% 
  select(final_afr_cue, afr_target) %>% 
  pivot_longer(cols = everything(),
               names_to = "type",
               values_to = "word") %>% 
  select(word)
```

## Lexical Data

```{r}
# length
DF$length <- nchar(DF$word)

# frequency processed with phonemes
subs_DF <- rio::import("subs_count/af/subs_DF_phono.csv") %>% 
  unique()

DF <- DF %>% 
  left_join(subs_DF, by = c("word" = "unigram"))

# orthographic neighborhood
DF <- calc_neighbors(DF, subs_DF)

# bigram frequency
DF <- add_bigram_frequency(DF, subs_DF, weight = "unigram_freq")

# orthographic Levenshtein
DF <- add_orthographic_levenshtein(DF, subs_DF, k = 20, max_len_diff = 3)

# phonographic Levenshtein
DF <- add_phonographic_levenshtein(DF, k = 20, max_len_diff = 3)

# semantic diversity
DF <- DF %>% 
  left_join(
    rio::import("semdiv_data/en/en_semantic_diversity.csv") %>% 
      select(-V1),
    by = c("word" = "term")
  )

# check out the NAs
```

## Subjective Data

```{r}
labData <- rio::import("../lab_variables_target_means.csv") %>%
  filter(grepl("afrikaans", word_column))
```

### AOA 

```{r}
Luniewska2015 <- rio::import("/Users/erinbuchanan/GitHub/Research/2_projects/SPAML/semanticprimeR/datasets/03.to_upload/Luniewska2015.csv") %>% 
  group_by(word_afrikaans) %>% 
  summarize(aoa_M = mean(aoa_M_afrikaans))

DF <- DF %>% 
  left_join(Luniewska2015, 
            by = c("word" = "word_afrikaans"))
```

### Imageability 

```{r}
DF$image <- NA
```

### Concrete

```{r}
DF$concrete <- NA
```

### Valence

```{r}
DF$valence <- NA
```

### Arousal

```{r}
DF$arousal <- NA
```
  
### Familiar

```{r}
DF$familiar <- NA
```

## Similarity Statistics

## Priming

### Human Prime

```{r}
# not ready yet 
```

### BERT Priming

## Embeddings

## Combine

```{r}

```

## Output Variable Match

```{r}
DF_var_match <- DF %>% 
  mutate(aoa = is.na(aoa_M)) %>% 
  select(word, aoa, image, concrete, valence, arousal, familiar) %>% 
  mutate(across(-word, ~replace_na(.x, FALSE)))

rio::export(DF_var_match, "af_variables_normed.csv", row.names = F)
```