---
title: "ML One Network: Norming Variable Power Analysis"
author: "The Doom Lab"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 8, fig.height = 5)
knitr::opts_knit$set(root.dir = normalizePath("."))

source("run_power_batch.R")
attach_required_packages()
load_shared_functions("functions.R")
library(ggplot2)
library(DT)

# `corrected_summary`/`overall_power` (semanticprimeR::calculate_correction)
# records, for each dataset run, the *achieved* percent_below nearest each
# requested power level (a near-continuous number like 76.85, not a clean
# 80) - but always in the fixed order of REFINE_POWER_LEVELS below, six rows
# per run. Grouping directly on the raw percent_below value (as
# load_and_summarize_simulations()'s own recommendation_summary does) treats
# every dataset's slightly-different achieved value as its own bin, so pools
# across datasets barely happen. Binning by position within each run
# recovers the intended target instead.
REFINE_POWER_LEVELS <- c(70, 75, 80, 85, 90, 95)

summarize_by_target <- function(overall_power, power_levels = REFINE_POWER_LEVELS) {
  overall_power %>%
    dplyr::group_by(run_id) %>%
    dplyr::mutate(target_power = power_levels[((dplyr::row_number() - 1) %% length(power_levels)) + 1]) %>%
    dplyr::ungroup() %>%
    dplyr::group_by(target_power) %>%
    dplyr::summarise(
      n_runs = sum(!is.na(corrected_sample_size)),
      mean_recommended_sample_size = mean(corrected_sample_size, na.rm = TRUE),
      median_recommended_sample_size = median(corrected_sample_size, na.rm = TRUE),
      sd_recommended_sample_size = sd(corrected_sample_size, na.rm = TRUE),
      min_recommended_sample_size = min(corrected_sample_size, na.rm = TRUE),
      max_recommended_sample_size = max(corrected_sample_size, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    dplyr::arrange(target_power) %>%
    dplyr::mutate(recommended_sample_size = ceiling(cummax(median_recommended_sample_size)))
}

label_by_target <- function(overall_power, power_levels = REFINE_POWER_LEVELS) {
  overall_power %>%
    dplyr::group_by(run_id) %>%
    dplyr::mutate(target_power = power_levels[((dplyr::row_number() - 1) %% length(power_levels)) + 1]) %>%
    dplyr::ungroup()
}

# Standard 1.5x IQR rule. Applied separately to the precision-recommended
# and reliability-recommended sample sizes for a variable, so a handful of
# very small/noisy source datasets (which can swing corrected_sample_size or
# the reliability-hit sample size wildly) don't dominate the average.
IQR_MULTIPLIER <- 1.5

iqr_bounds <- function(x, multiplier = IQR_MULTIPLIER) {
  x <- x[is.finite(x)]
  if (length(x) < 4) return(c(lower = -Inf, upper = Inf))
  qs <- stats::quantile(x, probs = c(0.25, 0.75), na.rm = TRUE, type = 7)
  iqr <- qs[[2]] - qs[[1]]
  c(lower = qs[[1]] - multiplier * iqr, upper = qs[[2]] + multiplier * iqr)
}

remove_iqr_outliers <- function(x, multiplier = IQR_MULTIPLIER) {
  x <- x[is.finite(x)]
  bounds <- iqr_bounds(x, multiplier)
  x[x >= bounds[["lower"]] & x <= bounds[["upper"]]]
}

n_at_precision_per_run <- function(overall_power, target_power = 80) {
  label_by_target(overall_power) %>%
    dplyr::filter(target_power == !!target_power) %>%
    dplyr::transmute(run_id, n_precision = corrected_sample_size)
}

n_at_reliability_per_run <- function(overall_rel, target_reliability = 0.80) {
  overall_rel %>%
    dplyr::mutate(
      reliability_m = as.numeric(reliability_m),
      sample_size = as.numeric(sample_size)
    ) %>%
    dplyr::filter(is.finite(reliability_m)) %>%
    dplyr::group_by(run_id) %>%
    dplyr::filter(reliability_m >= target_reliability) %>%
    dplyr::arrange(sample_size) %>%
    dplyr::slice_head(n = 1) %>%
    dplyr::ungroup() %>%
    dplyr::transmute(run_id, n_reliability = sample_size)
}

# For one variable: per-run n needed for target_power% precision and for
# target_reliability split-half reliability, IQR-outlier-trimmed separately,
# then averaged together into a single recommended sample size.
summarize_variable_recommendation <- function(res, target_power = 80, target_reliability = 0.80) {
  precision_per_run <- n_at_precision_per_run(res$overall_power, target_power)
  reliability_per_run <- n_at_reliability_per_run(res$overall_rel, target_reliability)

  precision_bounds <- iqr_bounds(precision_per_run$n_precision)
  reliability_bounds <- iqr_bounds(reliability_per_run$n_reliability)

  per_run <- precision_per_run %>%
    dplyr::full_join(reliability_per_run, by = "run_id") %>%
    dplyr::mutate(
      precision_outlier = is.finite(n_precision) &
        (n_precision < precision_bounds[["lower"]] | n_precision > precision_bounds[["upper"]]),
      reliability_outlier = is.finite(n_reliability) &
        (n_reliability < reliability_bounds[["lower"]] | n_reliability > reliability_bounds[["upper"]])
    )

  precision_clean <- per_run$n_precision[is.finite(per_run$n_precision) & !per_run$precision_outlier]
  reliability_clean <- per_run$n_reliability[is.finite(per_run$n_reliability) & !per_run$reliability_outlier]

  precision_median <- stats::median(precision_clean)
  reliability_median <- stats::median(reliability_clean)

  list(
    per_run = per_run,
    precision_n_total = nrow(precision_per_run),
    precision_n_kept = length(precision_clean),
    precision_median = precision_median,
    reliability_n_total = nrow(reliability_per_run),
    reliability_n_kept = length(reliability_clean),
    reliability_median = reliability_median,
    recommended_n = mean(c(precision_median, reliability_median))
  )
}
```

## Why this analysis exists

The ML One Network stimuli are scored on several norming variables collected
by SPAML/semanticprimeR contributor datasets: familiarity, concreteness,
valence, arousal, imageability, and age of acquisition (AoA). Before we
finalize how many raters we need per item for our own norming pass, we asked:
**given a target level of precision, how many participants per item are
needed to estimate the mean of a norming variable accurately, and how many
are needed for the item-level scores to be reliable?**

This is an *Accuracy in Parameter Estimation* (AIPE) question rather than a
traditional null-hypothesis-testing power question - we are not testing
whether a mean differs from zero, we are asking how large a sample needs to
be so that a *sample mean* lands acceptably close to the *true population
mean* for a given item. `functions.R` implements this using tools from the
`semanticprimeR` package: for each real dataset in
`power_job_list.csv`, item means/SDs are used to simulate a plausible
population distribution per item (`rtruncnorm`, bounded by the scale's
observed min/max), samples are repeatedly drawn from that simulated
population at increasing sample sizes, and for each sample size we compute:

- **percent below cutoff**: the proportion of simulated samples whose
  standard error falls under a precision cutoff (tighter error = more
  accurate estimate of the item mean).
- **corrected sample size**: the AIPE-corrected number of participants per
  item needed to reach a given target proportion (e.g., "95% of samples hit
  the precision cutoff").
- **split-half reliability**: participants for each item are split in half,
  the two half-means are correlated, and the correlation is Spearman-Brown
  corrected - this tells us how consistent the item-level scores would be
  with a given number of raters per item.

## Two-stage design: pilot then refine

Running a fine-grained simulation (many sample sizes x many simulations per
size) over every dataset up front would be slow, so the pipeline runs in two
stages (`run_power_pilot.R` then `run_power_refine.R`, both sourcing
`run_power_batch.R`):

1. **Pilot** - a coarse sweep per dataset (sample sizes 20-500, step 10, 10
   simulations per step) to find roughly where the precision curve crosses
   70% and 95% "hit" rates.
2. **Refine** - a narrow, high-precision rerun (step 5, 100 simulations per
   step) restricted to the pilot's recommended `[start, stop]` window for
   that specific dataset.

This document reads the **refined** stage output only, since that is the
higher-precision, final estimate. The pipeline currently covers six
variables:

```{r variables}
VARIABLES
```

## Target criteria and outlier handling

We target **80% power** (AIPE precision) and **80% split-half reliability**,
and report the recommended sample size per variable as the **average of
those two numbers**. Precision and reliability answer different questions
about the same design (how accurate is the estimated mean vs. how
consistent are the item scores), so averaging them gives one practical
number rather than always taking the stricter of the two.

Each of these numbers is computed **per dataset run** (i.e., per source
paper/corpus) before pooling: for a given variable, every dataset run
contributes one "n needed for 80% precision" value and one "n needed for
80% reliability" value. A handful of source datasets are small, noisy, or
otherwise unusual and can pull these per-run numbers to extreme highs or
lows. Before pooling across runs, we drop outlier runs using the standard
**1.5 x IQR rule** (values more than 1.5 interquartile ranges below Q1 or
above Q3 are dropped), applied separately to the precision values and the
reliability values for that variable. We then take the **median** of the
remaining runs for each metric (median rather than mean, since a handful of
runs can still sit near the trim boundary without being dropped outright -
in practice the two are close once outliers are trimmed, but median is the
more standard choice for a "typical" recommendation). The per-variable
sections below show which runs were flagged.

## Loading refined results

```{r load-results}
variable_dirs <- file.path("simulations", VARIABLES, "refined")
names(variable_dirs) <- VARIABLES
available_vars <- VARIABLES[dir.exists(variable_dirs) &
  lengths(purrr::map(variable_dirs, list.files, pattern = "\\.rds$")) > 0]

cat("Variables with refined output available:", paste(available_vars, collapse = ", "), "\n")
cat("Variables still pending:", paste(setdiff(VARIABLES, available_vars), collapse = ", "), "\n")

results_by_variable <- purrr::map(
  setNames(available_vars, available_vars),
  ~ load_and_summarize_simulations(file.path("simulations", .x, "refined"))
)
```

Each dataset contributes one simulation "run" per variable (i.e., one row
per source paper/corpus that reported that variable for the words in our
stimuli set). The tables below pool across *all* dataset runs for a
variable, since our own norming study will draw one sample of participants
per item, not one sample per source paper.

## Per-variable results

```{r per-variable-results, results='asis'}
target_results_by_variable <- purrr::map(results_by_variable, ~ summarize_by_target(.x$overall_power))
labeled_power_by_variable <- purrr::map(results_by_variable, ~ label_by_target(.x$overall_power))
variable_recommendation <- purrr::map(results_by_variable, ~ summarize_variable_recommendation(.x))

variable_labels <- c(
  familiar = "Familiarity", concrete = "Concreteness", valence = "Valence",
  arousal = "Arousal", imagine = "Imageability", aoa = "Age of Acquisition (AoA)"
)

for (v in available_vars) {
  cat(sprintf("\n### %s\n\n", variable_labels[[v]]))

  res <- results_by_variable[[v]]
  target_summary <- target_results_by_variable[[v]]
  n_runs <- dplyr::n_distinct(res$overall_power$run_id)
  cat(sprintf("Based on %d dataset run(s) for `%s`.\n\n", n_runs, v))

  cat("**Recommended sample size per item, by target precision (% of simulations hitting the AIPE cutoff):**\n\n")
  print(htmltools::tagList(DT::datatable(
    target_summary %>%
      dplyr::mutate(dplyr::across(where(is.numeric), ~ round(.x, 2))),
    rownames = FALSE, options = list(dom = "t", pageLength = 10)
  )))

  box_dat <- labeled_power_by_variable[[v]] %>%
    dplyr::mutate(target_power = factor(target_power, levels = REFINE_POWER_LEVELS))
  print(
    ggplot2::ggplot(box_dat, ggplot2::aes(x = target_power, y = corrected_sample_size)) +
      ggplot2::geom_boxplot(fill = "#d9e7ff", outlier.alpha = 0.2, width = 0.6) +
      ggplot2::geom_jitter(width = 0.12, alpha = 0.35, size = 1.4) +
      ggplot2::geom_line(
        data = target_summary %>% dplyr::mutate(target_power = factor(target_power, levels = REFINE_POWER_LEVELS)),
        ggplot2::aes(x = target_power, y = recommended_sample_size, group = 1),
        color = "#b00020", linewidth = 0.9
      ) +
      ggplot2::geom_point(
        data = target_summary %>% dplyr::mutate(target_power = factor(target_power, levels = REFINE_POWER_LEVELS)),
        ggplot2::aes(x = target_power, y = recommended_sample_size),
        color = "#b00020", size = 2.5
      ) +
      ggplot2::labs(
        x = "Target precision (%)", y = "Corrected sample size",
        title = paste0(v, ": spread of per-dataset recommendations"),
        subtitle = "red line = across-dataset running max of the median"
      ) +
      ggplot2::theme_minimal()
  )

  if (nrow(res$reliability_summary) > 0) {
    cat("\n\n**Sample size needed to reach target split-half reliability:**\n\n")
    print(htmltools::tagList(DT::datatable(
      res$reliability_recommendation %>%
        dplyr::mutate(dplyr::across(where(is.numeric), ~ round(.x, 3))),
      rownames = FALSE, options = list(dom = "t", pageLength = 10)
    )))

    if (!is.null(res$reliability_plot)) {
      print(res$reliability_plot +
        ggplot2::labs(subtitle = paste0(v, ": median reliability curve across dataset runs")))
    }
  }

  rec <- variable_recommendation[[v]]
  cat(sprintf(
    "\n\n**Recommended n (80%% precision + 80%% reliability, IQR-trimmed medians averaged): %.1f -> %d participants/item**\n\n",
    rec$recommended_n, ceiling(rec$recommended_n)
  ))
  cat(sprintf(
    "- Precision: %.1f (median of %d/%d runs kept after IQR trim)\n",
    rec$precision_median, rec$precision_n_kept, rec$precision_n_total
  ))
  cat(sprintf(
    "- Reliability: %.1f (median of %d/%d runs kept after IQR trim)\n",
    rec$reliability_median, rec$reliability_n_kept, rec$reliability_n_total
  ))

  cat("\n\n**Per-dataset detail (n at 80% precision, n at 80% reliability, outlier flags):**\n\n")
  print(htmltools::tagList(DT::datatable(
    rec$per_run %>%
      dplyr::mutate(dplyr::across(c(n_precision, n_reliability), ~ round(.x, 1))) %>%
      dplyr::arrange(dplyr::desc(n_precision)),
    rownames = FALSE, options = list(pageLength = 10)
  )))

  cat("\n\n---\n")
}
```

## Combined recommendation across variables

Our norming study collects all six variables from the same participants per
item, so the design has to satisfy every variable's IQR-trimmed 80/80
recommendation at once - the binding number is the **largest**
`recommended_n` across variables below.

```{r combined-summary}
combined_recommendation <- purrr::imap_dfr(variable_recommendation, function(rec, v) {
  tibble::tibble(
    variable = v,
    n_precision = rec$precision_median,
    precision_kept = sprintf("%d/%d", rec$precision_n_kept, rec$precision_n_total),
    n_reliability = rec$reliability_median,
    reliability_kept = sprintf("%d/%d", rec$reliability_n_kept, rec$reliability_n_total),
    recommended_n = rec$recommended_n
  )
})

combined_recommendation_display <- combined_recommendation %>%
  dplyr::mutate(dplyr::across(c(n_precision, n_reliability, recommended_n), ~ round(.x, 1))) %>%
  dplyr::arrange(dplyr::desc(recommended_n))

DT::datatable(combined_recommendation_display, rownames = FALSE, options = list(dom = "t", pageLength = 10))
```

```{r combined-plot, fig.height=4}
plot_dat <- combined_recommendation %>%
  dplyr::select(variable, n_precision, n_reliability) %>%
  tidyr::pivot_longer(c(n_precision, n_reliability), names_to = "metric", values_to = "n") %>%
  dplyr::mutate(metric = dplyr::recode(metric, n_precision = "80% precision", n_reliability = "80% reliability"))

ggplot2::ggplot(plot_dat, ggplot2::aes(x = reorder(variable, n), y = n, fill = metric)) +
  ggplot2::geom_col(position = ggplot2::position_dodge(width = 0.7), width = 0.6) +
  ggplot2::coord_flip() +
  ggplot2::labs(
    x = NULL, y = "Recommended sample size per item",
    fill = NULL,
    title = "IQR-trimmed median sample size per item, by variable and metric"
  ) +
  ggplot2::theme_minimal()
```

```{r overall-max}
overall_n_needed <- max(combined_recommendation$recommended_n, na.rm = TRUE)
overall_driver <- combined_recommendation$variable[[which.max(combined_recommendation$recommended_n)]]
overall_n_needed
```

**Bottom line:** averaging 80% precision and 80% reliability (after dropping
outlier dataset runs via the 1.5 x IQR rule) puts every variable's
recommended sample size at roughly **`r round(min(combined_recommendation$recommended_n))`-`r ceiling(overall_n_needed)`**
participants per item, with `r overall_driver` needing the most. Our norming
study needs at least **`r ceiling(overall_n_needed)`** participants per item
to satisfy every variable at once.

## Notes and caveats

- Precision and reliability are computed per dataset run and outlier-trimmed
  independently for each variable (see "Target criteria and outlier
  handling" above) - the per-variable sections show exactly which runs were
  dropped and why.
- `run_job()` in `run_power_batch.R` samples up to `max_rows` items per
  dataset (currently 1000) before simulating, and the refine stage runs
  `nsim` simulations per sample size (currently 500). If these are changed
  again, rerun the full pilot -> refine pipeline before re-knitting this
  document, since stale `.rds` output will silently make the numbers here
  wrong.
- A handful of individual split-half reliability draws come out as exactly
  -1.0 (perfect negative correlation on a small, noisy split), which sends
  the Spearman-Brown-corrected value to +/-Infinity for that one draw. This
  document filters those out via `is.finite()` before computing per-run
  reliability targets, so it doesn't affect the numbers above - flag it if
  a mean-based reliability figure is ever pulled from these `.rds` files
  some other way.
