---
title: "ML One Network: Norming Variable Power Analysis"
author: "The Doom Lab"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 8, fig.height = 5)
knitr::opts_knit$set(root.dir = normalizePath("."))

source("run_power_batch.R")
attach_required_packages()
load_shared_functions("functions.R")
library(ggplot2)
library(DT)

# `corrected_summary`/`overall_power` (semanticprimeR::calculate_correction)
# records, for each dataset run, the *achieved* percent_below nearest each
# requested power level (a near-continuous number like 76.85, not a clean
# 80) - but always in the fixed order of REFINE_POWER_LEVELS below, six rows
# per run. Grouping directly on the raw percent_below value (as
# load_and_summarize_simulations()'s own recommendation_summary does) treats
# every dataset's slightly-different achieved value as its own bin, so pools
# across datasets barely happen. Binning by position within each run
# recovers the intended target instead.
REFINE_POWER_LEVELS <- c(70, 75, 80, 85, 90, 95)

summarize_by_target <- function(overall_power, power_levels = REFINE_POWER_LEVELS) {
  overall_power %>%
    dplyr::group_by(run_id) %>%
    dplyr::mutate(target_power = power_levels[((dplyr::row_number() - 1) %% length(power_levels)) + 1]) %>%
    dplyr::ungroup() %>%
    dplyr::group_by(target_power) %>%
    dplyr::summarise(
      n_runs = sum(!is.na(corrected_sample_size)),
      mean_recommended_sample_size = mean(corrected_sample_size, na.rm = TRUE),
      median_recommended_sample_size = median(corrected_sample_size, na.rm = TRUE),
      sd_recommended_sample_size = sd(corrected_sample_size, na.rm = TRUE),
      min_recommended_sample_size = min(corrected_sample_size, na.rm = TRUE),
      max_recommended_sample_size = max(corrected_sample_size, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    dplyr::arrange(target_power) %>%
    dplyr::mutate(recommended_sample_size = ceiling(cummax(median_recommended_sample_size)))
}

label_by_target <- function(overall_power, power_levels = REFINE_POWER_LEVELS) {
  overall_power %>%
    dplyr::group_by(run_id) %>%
    dplyr::mutate(target_power = power_levels[((dplyr::row_number() - 1) %% length(power_levels)) + 1]) %>%
    dplyr::ungroup()
}
```

## Why this analysis exists

The ML One Network stimuli are scored on several norming variables collected
by SPAML/semanticprimeR contributor datasets: familiarity, concreteness,
valence, arousal, imageability, and age of acquisition (AoA). Before we
finalize how many raters we need per item for our own norming pass, we asked:
**given a target level of precision, how many participants per item are
needed to estimate the mean of a norming variable accurately, and how many
are needed for the item-level scores to be reliable?**

This is an *Accuracy in Parameter Estimation* (AIPE) question rather than a
traditional null-hypothesis-testing power question - we are not testing
whether a mean differs from zero, we are asking how large a sample needs to
be so that a *sample mean* lands acceptably close to the *true population
mean* for a given item. `functions.R` implements this using tools from the
`semanticprimeR` package: for each real dataset in
`power_job_list.csv`, item means/SDs are used to simulate a plausible
population distribution per item (`rtruncnorm`, bounded by the scale's
observed min/max), samples are repeatedly drawn from that simulated
population at increasing sample sizes, and for each sample size we compute:

- **percent below cutoff**: the proportion of simulated samples whose
  standard error falls under a precision cutoff (tighter error = more
  accurate estimate of the item mean).
- **corrected sample size**: the AIPE-corrected number of participants per
  item needed to reach a given target proportion (e.g., "95% of samples hit
  the precision cutoff").
- **split-half reliability**: participants for each item are split in half,
  the two half-means are correlated, and the correlation is Spearman-Brown
  corrected - this tells us how consistent the item-level scores would be
  with a given number of raters per item.

## Two-stage design: pilot then refine

Running a fine-grained simulation (many sample sizes x many simulations per
size) over every dataset up front would be slow, so the pipeline runs in two
stages (`run_power_pilot.R` then `run_power_refine.R`, both sourcing
`run_power_batch.R`):

1. **Pilot** - a coarse sweep per dataset (sample sizes 20-500, step 10, 10
   simulations per step) to find roughly where the precision curve crosses
   70% and 95% "hit" rates.
2. **Refine** - a narrow, high-precision rerun (step 5, 100 simulations per
   step) restricted to the pilot's recommended `[start, stop]` window for
   that specific dataset.

This document reads the **refined** stage output only, since that is the
higher-precision, final estimate. The pipeline currently covers six
variables:

```{r variables}
VARIABLES
```

## Loading refined results

```{r load-results}
variable_dirs <- file.path("simulations", VARIABLES, "refined")
names(variable_dirs) <- VARIABLES
available_vars <- VARIABLES[dir.exists(variable_dirs) &
  lengths(purrr::map(variable_dirs, list.files, pattern = "\\.rds$")) > 0]

cat("Variables with refined output available:", paste(available_vars, collapse = ", "), "\n")
cat("Variables still pending:", paste(setdiff(VARIABLES, available_vars), collapse = ", "), "\n")

results_by_variable <- purrr::map(
  setNames(available_vars, available_vars),
  ~ load_and_summarize_simulations(file.path("simulations", .x, "refined"))
)
```

Each dataset contributes one simulation "run" per variable (i.e., one row
per source paper/corpus that reported that variable for the words in our
stimuli set). The tables below pool across *all* dataset runs for a
variable, since our own norming study will draw one sample of participants
per item, not one sample per source paper.

## Per-variable results

```{r per-variable-results, results='asis'}
target_results_by_variable <- purrr::map(results_by_variable, ~ summarize_by_target(.x$overall_power))
labeled_power_by_variable <- purrr::map(results_by_variable, ~ label_by_target(.x$overall_power))

variable_labels <- c(
  familiar = "Familiarity", concrete = "Concreteness", valence = "Valence",
  arousal = "Arousal", imagine = "Imageability", aoa = "Age of Acquisition (AoA)"
)

for (v in available_vars) {
  cat(sprintf("\n### %s\n\n", variable_labels[[v]]))

  res <- results_by_variable[[v]]
  target_summary <- target_results_by_variable[[v]]
  n_runs <- dplyr::n_distinct(res$overall_power$run_id)
  cat(sprintf("Based on %d dataset run(s) for `%s`.\n\n", n_runs, v))

  cat("**Recommended sample size per item, by target precision (% of simulations hitting the AIPE cutoff):**\n\n")
  print(htmltools::tagList(DT::datatable(
    target_summary %>%
      dplyr::mutate(dplyr::across(where(is.numeric), ~ round(.x, 2))),
    rownames = FALSE, options = list(dom = "t", pageLength = 10)
  )))

  box_dat <- labeled_power_by_variable[[v]] %>%
    dplyr::mutate(target_power = factor(target_power, levels = REFINE_POWER_LEVELS))
  print(
    ggplot2::ggplot(box_dat, ggplot2::aes(x = target_power, y = corrected_sample_size)) +
      ggplot2::geom_boxplot(fill = "#d9e7ff", outlier.alpha = 0.2, width = 0.6) +
      ggplot2::geom_jitter(width = 0.12, alpha = 0.35, size = 1.4) +
      ggplot2::geom_line(
        data = target_summary %>% dplyr::mutate(target_power = factor(target_power, levels = REFINE_POWER_LEVELS)),
        ggplot2::aes(x = target_power, y = recommended_sample_size, group = 1),
        color = "#b00020", linewidth = 0.9
      ) +
      ggplot2::geom_point(
        data = target_summary %>% dplyr::mutate(target_power = factor(target_power, levels = REFINE_POWER_LEVELS)),
        ggplot2::aes(x = target_power, y = recommended_sample_size),
        color = "#b00020", size = 2.5
      ) +
      ggplot2::labs(
        x = "Target precision (%)", y = "Corrected sample size",
        title = paste0(v, ": spread of per-dataset recommendations"),
        subtitle = "red line = across-dataset running max of the median"
      ) +
      ggplot2::theme_minimal()
  )

  if (nrow(res$reliability_summary) > 0) {
    cat("\n\n**Sample size needed to reach target split-half reliability:**\n\n")
    print(htmltools::tagList(DT::datatable(
      res$reliability_recommendation %>%
        dplyr::mutate(dplyr::across(where(is.numeric), ~ round(.x, 3))),
      rownames = FALSE, options = list(dom = "t", pageLength = 10)
    )))

    if (!is.null(res$reliability_plot)) {
      print(res$reliability_plot +
        ggplot2::labs(subtitle = paste0(v, ": median reliability curve across dataset runs")))
    }
  }

  cat("\n\n**Per-dataset detail (recommended n at 80% target precision):**\n\n")
  per_dataset <- labeled_power_by_variable[[v]] %>%
    dplyr::filter(target_power == 80) %>%
    dplyr::select(run_id, corrected_sample_size) %>%
    dplyr::arrange(dplyr::desc(corrected_sample_size))
  print(htmltools::tagList(DT::datatable(
    per_dataset %>% dplyr::mutate(corrected_sample_size = round(corrected_sample_size, 1)),
    rownames = FALSE, options = list(pageLength = 10)
  )))

  cat("\n\n---\n")
}
```

## Combined recommendation across variables

Our norming study collects all variables from the same participants per
item, so the binding constraint is the **largest** recommended sample size
across variables and across *both* precision and reliability, not any single
variable's number. Precision (AIPE) and split-half reliability answer
different questions and don't move together at the same rate - the two
sections below show why.

### Precision (AIPE)

```{r combined-summary}
combined_power <- purrr::imap_dfr(target_results_by_variable, function(target_summary, v) {
  target_summary %>%
    dplyr::filter(target_power %in% c(80, 90, 95)) %>%
    dplyr::transmute(
      variable = v,
      target_precision = target_power,
      recommended_n = recommended_sample_size
    )
})

combined_power_wide <- combined_power %>%
  tidyr::pivot_wider(names_from = target_precision, values_from = recommended_n,
                      names_prefix = "n_at_") %>%
  dplyr::arrange(dplyr::desc(n_at_95))

DT::datatable(combined_power_wide, rownames = FALSE, options = list(dom = "t", pageLength = 10))
```

```{r combined-plot, fig.height=4}
plot_dat <- combined_power %>%
  dplyr::mutate(target_precision = factor(target_precision))

ggplot2::ggplot(plot_dat, ggplot2::aes(x = reorder(variable, recommended_n), y = recommended_n, fill = target_precision)) +
  ggplot2::geom_col(position = ggplot2::position_dodge(width = 0.7), width = 0.6) +
  ggplot2::coord_flip() +
  ggplot2::labs(
    x = NULL, y = "Recommended sample size per item",
    fill = "Target precision (%)",
    title = "Recommended sample size per item, by variable and target precision"
  ) +
  ggplot2::theme_minimal()
```

### Reliability (split-half, Spearman-Brown corrected)

Reliability climbs to an acceptable level much faster than precision does at
the *lower* targets - across all six variables it clears 0.80 by n=20-30
(the smallest sample sizes the refine stage actually tested). At the
strictest 95% target, though, it is not automatically dominated by
precision: see the bottom line below for which one actually binds once both
are compared directly.

```{r combined-reliability}
combined_reliability <- purrr::imap_dfr(results_by_variable, function(res, v) {
  if (nrow(res$reliability_recommendation) == 0) return(tibble::tibble())
  res$reliability_recommendation %>%
    dplyr::transmute(variable = v, target_reliability, recommended_sample_size)
})

combined_reliability_wide <- combined_reliability %>%
  tidyr::pivot_wider(names_from = target_reliability, values_from = recommended_sample_size,
                      names_prefix = "n_at_rel_") %>%
  dplyr::arrange(dplyr::desc(n_at_rel_0.95))

DT::datatable(combined_reliability_wide, rownames = FALSE, options = list(dom = "t", pageLength = 10))
```

```{r combined-reliability-plot, fig.height=4}
rel_plot_dat <- combined_reliability %>%
  dplyr::filter(target_reliability %in% c(0.8, 0.9, 0.95)) %>%
  dplyr::mutate(target_reliability = factor(target_reliability))

ggplot2::ggplot(rel_plot_dat, ggplot2::aes(x = reorder(variable, recommended_sample_size), y = recommended_sample_size, fill = target_reliability)) +
  ggplot2::geom_col(position = ggplot2::position_dodge(width = 0.7), width = 0.6) +
  ggplot2::coord_flip() +
  ggplot2::labs(
    x = NULL, y = "Recommended sample size per item",
    fill = "Target reliability",
    title = "Recommended sample size per item, by variable and target reliability"
  ) +
  ggplot2::theme_minimal()
```

```{r overall-max}
overall_n_precision <- max(combined_power_wide$n_at_95, na.rm = TRUE)
precision_driver <- combined_power_wide$variable[[which.max(combined_power_wide$n_at_95)]]

overall_n_reliability <- max(combined_reliability_wide$n_at_rel_0.95, na.rm = TRUE)
reliability_driver <- combined_reliability_wide$variable[[which.max(combined_reliability_wide$n_at_rel_0.95)]]

overall_n_needed <- max(overall_n_precision, overall_n_reliability, na.rm = TRUE)
binding_constraint <- if (overall_n_reliability > overall_n_precision) {
  sprintf("reliability (%s, needing %d for 0.95 reliability)", reliability_driver, overall_n_reliability)
} else {
  sprintf("precision (%s, needing %d for 95%% target precision)", precision_driver, overall_n_precision)
}
overall_n_needed
```

**Bottom line:** at the 95% target level the binding constraint is
`r binding_constraint`, not the other metric. Precision alone needs at
least **`r overall_n_precision`** participants per item (driven by
`r precision_driver`); reliability alone needs at least
**`r overall_n_reliability`** (driven by `r reliability_driver`). Combined
across both metrics and all six variables, our norming study needs at least
**`r overall_n_needed`** participants per item. If budget requires trading
precision for sample size, the per-variable tables show what's achievable at
80%/90% instead.

## Notes and caveats

- These recommendations are pooled across dataset runs that vary in scale,
  language, and item set - a per-dataset table is included above so outliers
  (e.g., unusually small or noisy source datasets) can be inspected directly.
- `run_job()` in `run_power_batch.R` currently subsamples any input dataset
  over 100 rows down to 100 rows before simulating. If that subsampling
  turns out to be unintentional, these numbers should be treated as
  provisional and rerun on the full item sets.
- AoA (`aoa`) is included in `VARIABLES` but its refined-stage simulation may
  not have finished yet - if it's missing from the results above, rerun this
  document after `run_power_refine.R` completes for `aoa`.
- A handful of individual split-half reliability draws come out as exactly
  -1.0 (perfect negative correlation on a small, noisy split), which sends
  the Spearman-Brown-corrected value to +/-Infinity and poisons
  `mean_reliability` for a few sample sizes in `valence`/`arousal`
  (visible if you inspect `overall_rel` directly). All reliability figures
  reported in this document use the median, which is unaffected - flag this
  if a mean-based reliability figure is ever pulled from these `.rds`
  files elsewhere.
