---
title: "ML One Network: Norming Variable Power Analysis"
author: "Erin M. Buchanan"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output:
    pdf_document
always_allow_html: true
bibliography: power_references.bib
  # html_document:
  #   toc: true
  #   toc_float: true
  #   code_folding: hide
  #   df_print: paged
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 8, fig.height = 5)
knitr::opts_knit$set(root.dir = normalizePath("."))

source("scripts/run_power_batch.R")
attach_required_packages()
load_shared_functions("scripts/functions.R")
library(ggplot2)
library(DT)

# `corrected_summary`/`overall_power` (semanticprimeR::calculate_correction)
# records, for each dataset run, the *achieved* percent_below nearest each
# requested power level (a near-continuous number like 76.85, not a clean
# 80) - but always in the fixed order of REFINE_POWER_LEVELS below, six rows
# per run. Grouping directly on the raw percent_below value (as
# load_and_summarize_simulations()'s own recommendation_summary does) treats
# every dataset's slightly-different achieved value as its own bin, so pools
# across datasets barely happen. Binning by position within each run
# recovers the intended target instead.
REFINE_POWER_LEVELS <- c(70, 75, 80, 85, 90, 95)

summarize_by_target <- function(overall_power, power_levels = REFINE_POWER_LEVELS) {
  overall_power %>%
    dplyr::group_by(run_id) %>%
    dplyr::mutate(target_power = power_levels[((dplyr::row_number() - 1) %% length(power_levels)) + 1]) %>%
    dplyr::ungroup() %>%
    dplyr::group_by(target_power) %>%
    dplyr::summarise(
      n_runs = sum(!is.na(corrected_sample_size)),
      mean_recommended_sample_size = mean(corrected_sample_size, na.rm = TRUE),
      median_recommended_sample_size = median(corrected_sample_size, na.rm = TRUE),
      sd_recommended_sample_size = sd(corrected_sample_size, na.rm = TRUE),
      min_recommended_sample_size = min(corrected_sample_size, na.rm = TRUE),
      max_recommended_sample_size = max(corrected_sample_size, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    dplyr::arrange(target_power) %>%
    dplyr::mutate(recommended_sample_size = ceiling(cummax(median_recommended_sample_size)))
}

label_by_target <- function(overall_power, power_levels = REFINE_POWER_LEVELS) {
  overall_power %>%
    dplyr::group_by(run_id) %>%
    dplyr::mutate(target_power = power_levels[((dplyr::row_number() - 1) %% length(power_levels)) + 1]) %>%
    dplyr::ungroup()
}

# Standard 1.5x IQR rule. Applied separately to the precision-recommended
# and reliability-recommended sample sizes for a variable, so a handful of
# very small/noisy source datasets (which can swing corrected_sample_size or
# the reliability-hit sample size wildly) don't dominate the average.
IQR_MULTIPLIER <- 1.5

iqr_bounds <- function(x, multiplier = IQR_MULTIPLIER) {
  x <- x[is.finite(x)]
  if (length(x) < 4) return(c(lower = -Inf, upper = Inf))
  qs <- stats::quantile(x, probs = c(0.25, 0.75), na.rm = TRUE, type = 7)
  iqr <- qs[[2]] - qs[[1]]
  c(lower = qs[[1]] - multiplier * iqr, upper = qs[[2]] + multiplier * iqr)
}

remove_iqr_outliers <- function(x, multiplier = IQR_MULTIPLIER) {
  x <- x[is.finite(x)]
  bounds <- iqr_bounds(x, multiplier)
  x[x >= bounds[["lower"]] & x <= bounds[["upper"]]]
}

n_at_precision_per_run <- function(overall_power, target_power = 80) {
  label_by_target(overall_power) %>%
    dplyr::filter(target_power == !!target_power) %>%
    dplyr::transmute(run_id, n_precision = corrected_sample_size)
}

n_at_reliability_per_run <- function(overall_rel, target_reliability = 0.80) {
  overall_rel %>%
    dplyr::mutate(
      reliability_m = as.numeric(reliability_m),
      sample_size = as.numeric(sample_size)
    ) %>%
    dplyr::filter(is.finite(reliability_m)) %>%
    dplyr::group_by(run_id) %>%
    dplyr::filter(reliability_m >= target_reliability) %>%
    dplyr::arrange(sample_size) %>%
    dplyr::slice_head(n = 1) %>%
    dplyr::ungroup() %>%
    dplyr::transmute(run_id, n_reliability = sample_size)
}

# For one variable: per-run n needed for target_power% precision and for
# target_reliability split-half reliability, IQR-outlier-trimmed separately,
# then averaged together into a single recommended sample size.
summarize_variable_recommendation <- function(res, target_power = 80, target_reliability = 0.80) {
  precision_per_run <- n_at_precision_per_run(res$overall_power, target_power)
  reliability_per_run <- n_at_reliability_per_run(res$overall_rel, target_reliability)

  precision_bounds <- iqr_bounds(precision_per_run$n_precision)
  reliability_bounds <- iqr_bounds(reliability_per_run$n_reliability)

  per_run <- precision_per_run %>%
    dplyr::full_join(reliability_per_run, by = "run_id") %>%
    dplyr::mutate(
      precision_outlier = is.finite(n_precision) &
        (n_precision < precision_bounds[["lower"]] | n_precision > precision_bounds[["upper"]]),
      reliability_outlier = is.finite(n_reliability) &
        (n_reliability < reliability_bounds[["lower"]] | n_reliability > reliability_bounds[["upper"]])
    )

  precision_clean <- per_run$n_precision[is.finite(per_run$n_precision) & !per_run$precision_outlier]
  reliability_clean <- per_run$n_reliability[is.finite(per_run$n_reliability) & !per_run$reliability_outlier]

  precision_median <- stats::median(precision_clean)
  reliability_median <- stats::median(reliability_clean)

  list(
    per_run = per_run,
    precision_n_total = nrow(precision_per_run),
    precision_n_kept = length(precision_clean),
    precision_median = precision_median,
    reliability_n_total = nrow(reliability_per_run),
    reliability_n_kept = length(reliability_clean),
    reliability_median = reliability_median,
    recommended_n = mean(c(precision_median, reliability_median))
  )
}
```

## Sample Size Estimation for Subjective Rating Variables

In a follow up to the Semantic Priming Across Many Languages
[@buchanan2025] project, we will collect data across 45
languages/variants on the following norming variables: familiarity,
concreteness, valence, arousal, imageability, and age of acquisition
(AoA). We will use the Buchanan et al. [-@buchanan2026] accuracy in
parameter estimation procedure to determine how many participants we
need to create a sufficiently narrow confidence interval around the mean
for each item. In this procedure, we use the following steps (reproduced
from original article):

### Step 1.

Use representative pilot data.

We included all norming datasets found in the original Linguistic
Annotated Bibiolography [@buchanan2019LABLinguisticAnnotated] and the
updated LAB workflow under construction at
<https://manynorms.many-languages.com>. We included datasets with our
target variables that included information about the mean and standard
deviation of each item. Datasets with only the mean were excluded, as we
could not simulate the data appropriately with no information about
variance. The original articles were reviewed for information on item
sample sizes, which was matched to the variables included in the
dataset. In cases of range estimates provided in the manuscript (i.e.,
15-20 people rated each item), we used the lower end of the range to
estimate with less precision (which would, in turn, increase sample size
requirements due to more uncertainty). The following datasets were used:

```{r dataset-citation-table, results='asis'}
dataset_variables <- read.csv("datasets_with_power_variables.csv", stringsAsFactors = FALSE)

dataset_citation_table <- dataset_variables %>%
  dplyr::mutate(
    bibtex_key = sub("\\.csv$", "", dataset),
    Reference = sprintf("[@%s]", bibtex_key),
    Variables = dplyr::case_when(
      TRUE ~ apply(
        dplyr::select(., familiar, concrete, valence, arousal, imagine, aoa), 1,
        function(row) paste(names(row)[row == "x" & !is.na(row)], collapse = ", ")
      )
    )
  ) %>%
  dplyr::transmute(Dataset = bibtex_key, Variables, Reference)

knitr::kable(dataset_citation_table, row.names = FALSE)
```

### Step 2.

Calculate the standard error of each of the items in the pilot data.
Using the 4th decile, determine the cutoff and stopping rule for the
standard error of the items.

Using the *semanticprimeR* package [@buchanan2024], we then simulated
the pilot data using the mean, standard deviation, and sample size from
each dataset for the items included. This dataset was treated as the
"population", and we estimated the 4th decile standard error across all
items as the cutoff score and stopping rule for the standard error of
the items.

### Step 3.

Create simulated samples of your pilot data, starting with at least 20
participants, up to a maximum number of participants.

We then sampled from the simulated pilot data, from *n* = 20 up to *n* =
500. However, running the simulation over many samples by many
simulations by every dataset would be extremely slow. Therefore, we
broke the simulations into two stages:

1.  Pilot - a coarse sweep per dataset (sample sizes 20-500, step 10, 10
    simulations per step) to find roughly where the precision curve
    crosses 70% and 95% rates. `run_power_pilot.R`
2.  Refine - a narrow, high-precision rerun (step 5, 100 simulations per
    step) restricted to the pilot's recommended `[start, stop]` window
    for that specific dataset. `run_power_refine.R`

Both of these scripts call `run_power_batch.R` to do the simulations.
This document reads the refined stage output only, since that is the
higher-precision, final estimate.

### Step 4.

Calculate the standard error of each of the items in the simulated data.
From these scores, calculate the percent of items below the cutoff score
from Step 2.

### Step 5.

Determine the sample size at which 80%, 85%, 90%, 95% of items are below
the cutoff score. Use the correction formula to adjust your proposed
sample size based on pilot data size, power, and percent variability.

`functions.R` implements steps 3-5 using tools from the `semanticprimeR`
package for each real dataset in `power_job_list.csv`.

### Step 6.

Report all values. Designate one as the minimum sample size, the cutoff
score as the stopping rule for adaptive designs, and the maximum sample
size.

### Split-half Reliability

We additionally included a calculation of split-half reliability for
each of the sample sizes. Participants for each item are split in half,
the two half-means are correlated, and the Spearman-Brown correction is
then applied. This result tells us how consistent the item-level scores
would be with a given number of raters per item. Generally, numbers can
be very low and obtain reliability. We tested reliability at sample
sizes of *n* = 5 to the stop of the range found for each dataset from
the pilot sample size estimation steps.

## Target Criteria and Outlier Handling

We target 80% power (AIPE precision) and 80% split-half reliability, and
report the recommended sample size per variable as the average of those
two numbers. Precision and reliability answer different questions about
the same design (how accurately measured is the estimated mean vs. how
consistent are the item scores), so averaging them gives one practical
number rather than always taking the stricter of the two. We tested *n*
= 5, but set the bottom value for reliability to be *n* = 20. Therefore,
that means even if samples achieved high reliability at *n* = 5, 10, or
15, the lowest number we would accept for the average of criterions
would be *n* = 20, as otherwise the low numbers might bias the sample
size estimates downward inappropriately.

Each of these numbers is computed per dataset run (i.e., per source
paper/corpus) before pooling: for a given variable, every dataset run
contributes one "n needed for 80% precision" value and one "n needed for
80% reliability" value. A handful of source datasets are small, noisy,
or otherwise unusual and can pull these per-run numbers to extreme highs
or lows. Before pooling across runs, we drop outlier runs using the
standard 1.5 x IQR rule (values more than 1.5 interquartile ranges below
Q1 or above Q3 are dropped), applied separately to the precision values
and the reliability values for that variable. We then take the median of
the remaining runs for each metric (median rather than mean, since a
handful of runs can still sit near the outlier boundary without being
dropped outright - in practice the two are close once outliers are
trimmed, but median is the more standard choice for a "typical"
recommendation). The per-variable sections below show which runs were
considered outliers.

## Loading Refined Results

```{r load-results}
variable_dirs <- file.path("simulations", VARIABLES, "refined")
names(variable_dirs) <- VARIABLES
available_vars <- VARIABLES[dir.exists(variable_dirs) &
  lengths(purrr::map(variable_dirs, list.files, pattern = "\\.rds$")) > 0]

cat("Variables with refined output available:", paste(available_vars, collapse = ", "), "\n")
cat("Variables still pending:", paste(setdiff(VARIABLES, available_vars), collapse = ", "), "\n")

results_by_variable <- purrr::map(
  setNames(available_vars, available_vars),
  ~ load_and_summarize_simulations(file.path("simulations", .x, "refined"))
)
```

Each dataset contributes one simulation "run" per variable (i.e., one
row per source paper/corpus that reported that variable for the words in
our stimuli set). The tables below pool across *all* dataset runs for a
variable, since our own norming study will draw one sample of
participants per item. Each of these datasets is a mix of languages, so
we estimate our overall sample size globally, rather than by language.

## Per-Variable Results

```{r per-variable-results, results='asis'}
target_results_by_variable <- purrr::map(results_by_variable, ~ summarize_by_target(.x$overall_power))
labeled_power_by_variable <- purrr::map(results_by_variable, ~ label_by_target(.x$overall_power))
variable_recommendation <- purrr::map(results_by_variable, ~ summarize_variable_recommendation(.x))

variable_labels <- c(
  familiar = "Familiarity", concrete = "Concreteness", valence = "Valence",
  arousal = "Arousal", imagine = "Imageability", aoa = "Age of Acquisition (AoA)"
)

for (v in available_vars) {
  cat(sprintf("\n### %s\n\n", variable_labels[[v]]))

  res <- results_by_variable[[v]]
  target_summary <- target_results_by_variable[[v]]
  n_runs <- dplyr::n_distinct(res$overall_power$run_id)
  cat(sprintf("Based on %d dataset run(s) for `%s`.\n\n", n_runs, v))

  cat("**Recommended sample size per item, by target precision (% of simulations hitting the AIPE cutoff):**\n\n")
  print(htmltools::tagList(DT::datatable(
    target_summary %>%
      dplyr::mutate(dplyr::across(where(is.numeric), ~ round(.x, 2))),
    rownames = FALSE, options = list(dom = "t", pageLength = 10)
  )))

  box_dat <- labeled_power_by_variable[[v]] %>%
    dplyr::mutate(target_power = factor(target_power, levels = REFINE_POWER_LEVELS))
  print(
    ggplot2::ggplot(box_dat, ggplot2::aes(x = target_power, y = corrected_sample_size)) +
      ggplot2::geom_boxplot(fill = "#d9e7ff", outlier.alpha = 0.2, width = 0.6) +
      ggplot2::geom_jitter(width = 0.12, alpha = 0.35, size = 1.4) +
      ggplot2::geom_line(
        data = target_summary %>% dplyr::mutate(target_power = factor(target_power, levels = REFINE_POWER_LEVELS)),
        ggplot2::aes(x = target_power, y = recommended_sample_size, group = 1),
        color = "#b00020", linewidth = 0.9
      ) +
      ggplot2::geom_point(
        data = target_summary %>% dplyr::mutate(target_power = factor(target_power, levels = REFINE_POWER_LEVELS)),
        ggplot2::aes(x = target_power, y = recommended_sample_size),
        color = "#b00020", size = 2.5
      ) +
      ggplot2::labs(
        x = "Target precision (%)", y = "Corrected sample size",
        title = paste0(v, ": spread of per-dataset recommendations"),
        subtitle = "red line = across-dataset running max of the median"
      ) +
      ggplot2::theme_minimal()
  )

  if (nrow(res$reliability_summary) > 0) {
    cat("\n\n**Sample size needed to reach target split-half reliability:**\n\n")
    print(htmltools::tagList(DT::datatable(
      res$reliability_recommendation %>%
        dplyr::mutate(dplyr::across(where(is.numeric), ~ round(.x, 3))),
      rownames = FALSE, options = list(dom = "t", pageLength = 10)
    )))

    if (!is.null(res$reliability_plot)) {
      print(res$reliability_plot +
        ggplot2::labs(subtitle = paste0(v, ": median reliability curve across dataset runs")))
    }
  }

  rec <- variable_recommendation[[v]]
  cat(sprintf(
    "\n\n**Recommended n (80%% precision + 80%% reliability, IQR-trimmed medians averaged): %.1f -> %d participants/item**\n\n",
    rec$recommended_n, ceiling(rec$recommended_n)
  ))
  cat(sprintf(
    "- Precision: %.1f (median of %d/%d runs kept after IQR trim)\n",
    rec$precision_median, rec$precision_n_kept, rec$precision_n_total
  ))
  cat(sprintf(
    "- Reliability: %.1f (median of %d/%d runs kept after IQR trim)\n",
    rec$reliability_median, rec$reliability_n_kept, rec$reliability_n_total
  ))

  cat("\n\n**Per-dataset detail (n at 80% precision, n at 80% reliability, outlier flags):**\n\n")
  print(htmltools::tagList(DT::datatable(
    rec$per_run %>%
      dplyr::mutate(dplyr::across(c(n_precision, n_reliability), ~ round(.x, 1))) %>%
      dplyr::arrange(dplyr::desc(n_precision)),
    rownames = FALSE, options = list(pageLength = 10)
  )))

  cat("\n\n---\n")
}
```

## Combined Recommendation Across Variables

Our norming study collects all six variables from the same participants
per item, so the design has to satisfy every variable's IQR-trimmed
80/80 recommendation at once - the number is the largest `recommended_n`
across variables below.

```{r combined-summary}
combined_recommendation <- purrr::imap_dfr(variable_recommendation, function(rec, v) {
  tibble::tibble(
    variable = v,
    n_precision = rec$precision_median,
    precision_kept = sprintf("%d/%d", rec$precision_n_kept, rec$precision_n_total),
    n_reliability = rec$reliability_median,
    reliability_kept = sprintf("%d/%d", rec$reliability_n_kept, rec$reliability_n_total),
    recommended_n = rec$recommended_n
  )
})

combined_recommendation_display <- combined_recommendation %>%
  dplyr::mutate(dplyr::across(c(n_precision, n_reliability, recommended_n), ~ round(.x, 1))) %>%
  dplyr::arrange(dplyr::desc(recommended_n))

DT::datatable(combined_recommendation_display, rownames = FALSE, options = list(dom = "t", pageLength = 10))
```

```{r combined-plot, fig.height=4}
plot_dat <- combined_recommendation %>%
  dplyr::select(variable, n_precision, n_reliability) %>%
  tidyr::pivot_longer(c(n_precision, n_reliability), names_to = "metric", values_to = "n") %>%
  dplyr::mutate(metric = dplyr::recode(metric, n_precision = "80% precision", n_reliability = "80% reliability"))

ggplot2::ggplot(plot_dat, ggplot2::aes(x = reorder(variable, n), y = n, fill = metric)) +
  ggplot2::geom_col(position = ggplot2::position_dodge(width = 0.7), width = 0.6) +
  ggplot2::coord_flip() +
  ggplot2::labs(
    x = NULL, y = "Recommended sample size per item",
    fill = NULL,
    title = "IQR-trimmed median sample size per item, by variable and metric"
  ) +
  ggplot2::theme_minimal()
```

```{r overall-max}
overall_n_needed <- max(combined_recommendation$recommended_n, na.rm = TRUE)
overall_driver <- combined_recommendation$variable[[which.max(combined_recommendation$recommended_n)]]
overall_n_needed
```

Bottom line: averaging 80% precision and 80% reliability (after dropping
outlier dataset runs via the 1.5 x IQR rule) puts every variable's
recommended sample size at roughly
`r round(min(combined_recommendation$recommended_n))`-`r ceiling(overall_n_needed)`
participants per item, with `r overall_driver` needing the most. Our
norming study needs at least `r ceiling(overall_n_needed)` participants
per item to satisfy every variable at once.

## References
